---
title: "30-Day Low Flow Metric"
author: "Alex Lowe"
date: "6/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## What is the 30-Day Low Flow?

The 30-Day Low Flow metric is the average of the lowest 30 consecutive days of flow rate collected during a certain time period. The time period can be seasonal, yearly, and longer.

The 30-Day Low Flow is a low flow metric used to quantify changes in the magnitude, frequency, timing, rate-of-change and duration of drought flows. Because it consists of 30-days worth of data, it is used specifically for monthly flows.

This metric can also be used to create more metrics, such as the 30Q2, 30Q10, and more. The 30Q2 is the lowest expected 30 day average flow over a 2 year period. Similarly, the 30Q10 is the lowest expected 30 day average flow over a 10 year period.

Yearly 30-Day low flow values can be calculated in R by using the group2() function in the IHA package. Below is a sample of code that generates a table which includes 30-Day Low Flow values of a USGS site's gage data

```
datesp <- rawDailyp$Date
zoorawDailyp <- zoo(x=rawDailyp$X_00060_00003, order.by = datesp)
tablep <- group2(zoorawDailyp, year=c('water'),mimic.tnc=T)                              
```

### Blackwater River in Dendron, VA
#### Site ID: 02047500
```{r echo=FALSE, message=FALSE}
library(zoo)
library(IHA)
library(ggplot2)
library(dataRetrieval)

#Dendron, VA
site_idva <- '02047500'
pCode <- '00060'
startDate = '1999-10-01'
endDate = '2019-09-30'

siteinfova <- readNWISsite(site_idva)
rawDailyva2 <- readNWISdv(site_idva,pCode,startDate,endDate)

datesva <- rawDailyva2$Date
zoorawDailyva2 <- zoo(x=rawDailyva2$X_00060_00003, order.by = datesva)
tableva <- group2(zoorawDailyva2, year=c('water'),mimic.tnc = T)
ggplot(NULL, aes(x=tableva$year, tableva$`30 Day Min`))+
  geom_line()+
  theme_bw()+
  labs( title = '30-Day Low Flows by year in Dendron, VA', x = 'Year', y = 'Discharge (cfs)') +
  theme(plot.title = element_text(face = 'bold',hjust = 0.5))
```

### Potomac River near Washington, DC
#### Site ID: 01646502
```{r echo=FALSE}
library(zoo)
library(IHA)
library(ggplot2)
library(dataRetrieval)


pCode <- '00060'
#Potomac, VA
site_idp <- '01646502'
startDate = '1999-10-01'
endDate = '2019-09-30'

siteinfop <- readNWISsite(site_idp)
rawDailyp <- readNWISdv(site_idp,pCode,startDate,endDate)

datesp <- rawDailyp$Date
zoorawDailyp <- zoo(x=rawDailyp$X_00060_00003, order.by = datesp)
tablep <- group2(zoorawDailyp, year=c('water'),mimic.tnc=T)
ggplot(NULL, aes(x=tablep$year, tablep$`30 Day Min`))+
  geom_line()+
  theme_bw()+
  labs( title = '30-Day Low Flows by year on the Potomac', x = 'Year', y = 'Discharge (cfs)') +
  theme(plot.title = element_text(face = 'bold',hjust = 0.5))
```

### Holston River in Damascus, VA
#### Site ID: 03473000
```{r echo=FALSE}
library(zoo)
library(IHA)
library(ggplot2)
library(dataRetrieval)

pCode <- '00060'
#Holston, VA
site_idh <- '03473000'
startDate = '1999-10-01'
endDate = '2019-09-30'

siteinfoh <- readNWISsite(site_idh)
rawDailyh <- readNWISdv(site_idh,pCode,startDate,endDate)

datesh <- rawDailyh$Date
zoorawDailyh <- zoo(x=rawDailyh$X_00060_00003, order.by = datesh)
tableh <- group2(zoorawDailyh, year=c('water'),mimic.tnc=T)
ggplot(NULL, aes(x=tableh$year, tableh$`30 Day Min`))+
  geom_line()+
  theme_bw()+
  labs( title = '30-Day Low Flows by year on the Holston River', x = 'Year', y = 'Discharge (cfs)') +
  theme(plot.title = element_text(face = 'bold',hjust = 0.5))
```

### South River near Waynesboro, VA
#### Site ID: 01626000
```{r echo=FALSE}
library(zoo)
library(IHA)
library(ggplot2)
library(dataRetrieval)

pCode <- '00060'
#Sarah
site_ids <- '01626000'
startDate = '1999-10-01'
endDate = '2019-09-30'

siteinfos <- readNWISsite(site_ids)
rawDailys <- readNWISdv(site_ids,pCode,startDate,endDate)

datess <- rawDailys$Date
zoorawDailys <- zoo(x=rawDailys$X_00060_00003, order.by = datess)
tables <- group2(zoorawDailys, year=c('water'),mimic.tnc=T)
ggplot(NULL, aes(x=tables$year, tables$`30 Day Min`))+
  geom_line()+
  theme_bw()+
  labs( title = '30-Day Low Flows by year on the South River', x = 'Year', y = 'Discharge (cfs)') +
  theme(plot.title = element_text(face = 'bold',hjust = 0.5))
```

### Appomatox River in Mattoax, VA
#### Site ID: 02040000
```{r echo=FALSE}
library(zoo)
library(IHA)
library(ggplot2)
library(dataRetrieval)

pCode <- '00060'
#Miriam
site_idm <- '02040000'
startDate = '1999-10-01'
endDate = '2019-09-30'

siteinfom <- readNWISsite(site_idm)
rawDailym <- readNWISdv(site_idm,pCode,startDate,endDate)

datesm <- rawDailym$Date
zoorawDailym <- zoo(x=rawDailym$X_00060_00003, order.by = datesm)
tablem <- group2(zoorawDailym, year=c('water'),mimic.tnc=T)
ggplot(NULL, aes(x=tablem$year, tablem$`30 Day Min`))+
  geom_line()+
  theme_bw()+
  labs( title = '30-Day Low Flows by year on the Appomattox River', x = 'Year', y = 'Discharge (cfs)') +
  theme(plot.title = element_text(face = 'bold',hjust = 0.5))
```

### Comarison Plots
The Potomac River was left out of the comparison plots because its low flow values were much larger than the other rivers
```{r echo=FALSE, message=FALSE}
library(readr)
library(ggplot2)
library(IHA)
library(dataRetrieval)
library(dplyr)
library(scales)
library(zoo)

#Dendron, VA
site_idva <- '02047500'
pCode <- '00060'
#Potomac, VA
site_idp <- '01646502'
#Holston, VA
site_idh <- '03473000'
#Sarah
site_ids <- '01626000'
#Miriam
site_idm <- '02040000'

#Start Date and End Date
startDate = '1999-10-01'
endDate = '2019-09-30'

#Extracting and reading gage data for each site
siteinfova <- readNWISsite(site_idva)
siteinfop <- readNWISsite(site_idp)
siteinfoh <- readNWISsite(site_idh)
siteinfos <- readNWISsite(site_ids)
siteinfom <- readNWISsite(site_idm)

rawDailyva2 <- readNWISdv(site_idva,pCode,startDate,endDate)
rawDailyp <- readNWISdv(site_idp,pCode,startDate,endDate)
rawDailyh <- readNWISdv(site_idh,pCode,startDate,endDate)
rawDailys <- readNWISdv(site_ids,pCode,startDate,endDate)
rawDailym <- readNWISdv(site_idm,pCode,startDate,endDate)

#Alex (dendron)
datesva <- rawDailyva2$Date
zoorawDailyva2 <- zoo(x=rawDailyva2$X_00060_00003, order.by = datesva)
tableva <- group2(zoorawDailyva2, year=c('water'),mimic.tnc = T)

#Natty (Potomac)
datesp <- rawDailyp$Date
zoorawDailyp <- zoo(x=rawDailyp$X_00060_00003, order.by = datesp)
tablep <- group2(zoorawDailyp, year=c('water'),mimic.tnc=T)

#Kyle (Holtsten)
datesh <- rawDailyh$Date
zoorawDailyh <- zoo(x=rawDailyh$X_00060_00003, order.by = datesh)
tableh <- group2(zoorawDailyh, year=c('water'),mimic.tnc=T)

#Sarah
datess <- rawDailys$Date
zoorawDailys <- zoo(x=rawDailys$X_00060_00003, order.by = datess)
tables <- group2(zoorawDailys, year=c('water'),mimic.tnc=T)

#Miriam
datesm <- rawDailym$Date
zoorawDailym <- zoo(x=rawDailym$X_00060_00003, order.by = datesm)
tablem <- group2(zoorawDailym, year=c('water'),mimic.tnc=T)

#Comparison Line Graph (Excluded the Potomac because it was so big)
ggplot(NULL, aes(x=tables$year))+
  geom_line(aes(y=tableva$`30 Day Min`, color='Blackwater River'))+
  geom_line(aes(y=tablem$`30 Day Min`, color='Appomatox River'))+
  geom_line(aes(y=tableh$`30 Day Min`, color='Holston River'))+
  geom_line(aes(y=tables$`30 Day Min`, color='South River'))+
  theme_bw()+
  labs( title = 'Comparison Plot of 30-Day Low Flows by year', x = 'Year', y = 'Discharge (cfs)') +
  theme(plot.title = element_text(face = 'bold',hjust = 0.5))

#Comparison Box Plot
tableT <- rbind(tableva,tableh,tables,tablem)
length.data <- 1:20
tableT$River <- c(rep('Blackwater River', length(length.data)), rep('Holston River', length(length.data)), rep('South River', length(length.data)), rep('Appomatox River', length(length.data)))
tableT$River <- factor(tableT$River, levels=c('Blackwater River','Holston River','South River','Appomatox River'))
ggplot(NULL, aes(x=tableT$River, y=tableT$`30 Day Min`))+
  geom_boxplot(outlier.shape=NA)+
  geom_point(color='red',stat='summary',fun='mean')+
  theme_bw()+
  labs( title = '30-Day Low Flows between Locations from past 20 Water Years', x = 'Location', y = 'Discharge (cfs)') +
  theme(plot.title = element_text(face = 'bold',hjust = 0.5))+
  coord_cartesian(ylim=c(0,225))
```


## 30Q2
30Q2 is a metric that describes the lowest 30-day average flow likely to occur over a 2 year period.

30Q2 is computed by taking the 30-day flow average for a period of time, usually at least 20 years. The annual minimums of these averages are fit to a log-Pearson III distribution curve. The distribution is then analyzed for an adjusted probability to find the flow representative of 0.5 probability.

30Q2 can be calculated in R by using the PearsonDS package. Below is a sample of code that generates a 30Q2 value using the 30-Day minimum table created in the above sample.

```
tablep30Q <- as.vector(as.matrix(tablep['30 Day Min']))
tablep30Q <- log(tablep30Q)
parsp30 <- PearsonDS:::pearsonIIIfitML(tablep30Q)
p30Q2 <- exp(qpearsonIII(0.5, params = parsp30$par))                                     
```

Location | 30Q2 based on the last 20 water years (cfs)
-------- | ----
Potomac River | 2448.3
Holston River | 115.48
South River | 31.941
Appomatox River | 77.655