---
date: "`r format(Sys.time(), '%m/%d/%Y')`"
author: ""
title: "`r params$doc_title`"
output: 
  officedown::rdocx_document:
    mapstyles:
      Normal: ['First Paragraph']
    page_margins:
      bottom: 0.5
      top: 0.5
      right: 1
      left: 0.5
      header: 0.0
      footer: 0.0
params: 
  doc_title: "Comparison of Two VaHydro Models"
  rseg.file.path: [ "/media/model/p6/out/river/hsp2_2022/hydr/JA4_7280_7340_hydrd_wy.csv", "/media/model/p6/out/river/subsheds/hydr/JA4_7280_7340_hydrd_wy.csv" ]
  #rseg.hydrocode: [ "JA4_7280_7340","vahydrosw_wshed_JA4_7280_7340" ]
  #rseg.ftype: [ "cbp60","vahydro" ]
  #rseg.model.version: [ "cbp-6.0","cbp-6.1" ]
  #runid.list: [ "hsp2_2022","subsheds" ]
  rseg.metric.list: [ "Qout","l90_Qout","l30_Qout","l07_Qout","l01_Qout","consumptive_use_frac","wd_cumulative_mgd","ps_cumulative_mgd","wd_mgd","ps_mgd" ]

  rseg.hydrocode: [ "JL1_7202_7200", "vahydrosw_wshed_JL1_7202_7200" ] #Black Creek Reservoir
  rseg.ftype: [ "vahydro", "vahydro"]
  rseg.model.version: [ "cbp-6.1", "cbp-6.1"]
  runid.list: ["subsheds", "p6ss"]
---

```{r setup, include=FALSE}
#https://cran.r-project.org/web/packages/officedown/officedown.pdf
#https://ardata-fr.github.io/officeverse/officedown-for-word.html#insert-sections
knitr::opts_chunk$set(echo = TRUE, fig.cap = TRUE)
library(officedown)
library(officer)
library(flextable)
library(hydrotools)
library(rjson)
library(cowplot)
library(gridExtra)
library(tidyr)
library(ggplot2)
library(dplyr)
basepath='/var/www/R'
source('/var/www/R/config.R')

site <- 'http://deq1.bse.vt.edu/d.dh'
json_obj_url <- paste(site, "node/62", sep ="/")

ds <- RomDataSource$new("http://deq1.bse.vt.edu/d.dh", rest_uname)
ds$get_token(rest_pw)
# Load functions used during development
source("https://raw.githubusercontent.com/HARPgroup/hydro-tools/master/VAHydro-2.0/fn_get_prop.R")
source("https://raw.githubusercontent.com/HARPgroup/hydro-tools/master/VAHydro-2.0/rest_functions.R")
source("https://raw.githubusercontent.com/HARPgroup/hydro-tools/master/VAHydro-2.0/find_name.R")

fp <- fp_par(
  text.align = "center", 
  padding.bottom = 20, padding.top = 120, 
  border.bottom = fp_border())

ft <- fp_text(shading.color='#EFEFEF', bold = TRUE)

```

# Table of contents
```{r, echo = FALSE}
block_toc()
```

```{r UserInputs, include=FALSE}
rseg.filepath <- params$rseg.file.path
rseg.hydrocode <- params$rseg.hydrocode
rseg.ftype <- params$rseg.ftype
rseg.model.version <- params$rseg.model.version
runid.list <- params$runid.list
rseg.metric.list <- params$rseg.metric.list

rlist <- gsub('runid_', '', runid.list)

# r <- 1
for (r in 1:length(rseg.model.version)){
  
  # get rseg feature
  rseg.hydrocode.r <- rseg.hydrocode[r]
  rseg.ftype.r <- rseg.ftype[r]
  rseg_feature <- RomFeature$new(
    ds,
    list(hydrocode = rseg.hydrocode.r, ftype = rseg.ftype.r),
    TRUE
  )
  rseg.hydroid.r <- rseg_feature$hydroid
  
  # get rseg model
  rseg.model.version.r <- rseg.model.version[r]
  print(paste("searching", rseg.model.version.r,"model for river segment hydroid", rseg.hydroid.r))
  rseg.model.r <- RomProperty$new(
    ds,
    list(entity_type='dh_feature', featureid = rseg.hydroid.r, propcode=rseg.model.version.r),
    TRUE
  )
  
  if (exists("json_obj_url")) {
  rseg_obj_url.r <- paste(json_obj_url, rseg.model.r$pid, sep="/")
  rseg_model_info.r <- ds$auth_read(rseg_obj_url.r, "text/json", "")
  rseg_model_info.r <- fromJSON(rseg_model_info.r)
  } else {
  message("Error: json_obj_url is undefined.  Can not retrieve model and scenario information. (Hint: Use config.R
          to set json_obj_url) ")
  rseg_model_info.r <- list()
  }
  
  # stash the model run data into a combined list
  if (r == 1){
    dat <- rseg_model_info.r
  } else {
    dat <- cbind(dat,rseg_model_info.r)
  }
  
  # retrieve metrics for a run
  runid.r <- runid.list[r]
  rseg_table.r <- om_model_table(model_info = rseg_model_info.r,
                             runid.list = runid.r,
                             metric.list = rseg.metric.list,
                             include.elfgen = TRUE,
                             site = site,
                             site_base = omsite
                             )

  # join results from multiple runs to a single dataframe & create captioning for later
  if (r == 1){
    rseg_metrics.df <- rseg_table.r
  } else {
    rseg_metrics.df <- cbind(rseg_metrics.df,rseg_table.r)
  }

}

 <- qflextable(statsdf)

```

The models compared in this document are:
``` {r modelinfo, echo = FALSE, tab.cap = 'Properties of each model compared in this document.', tab.id="modelinfo"}
for (r in 1:length(rseg.model.version)){
  ftext.model.r <- paste(rseg_model_info.r[[1]][[3]])
  ftext.hcode.r <- paste(rseg.hydrocode.r)
  ftext.ftype.r <- paste(rseg.ftype.r)
  ftext.version.r <- paste(rseg.model.version.r)
  ftext.id.r <- paste(runid.r)
  
  if (r == 1){
    model.num <- paste("Model", r)
    ftext.model <- ftext.model.r 
    ftext.hcode <- ftext.hcode.r 
    ftext.ftype <- ftext.ftype.r 
    ftext.version <- ftext.version.r 
    ftext.id <- ftext.id.r
    title_param <- paste(ftext.model.r)
  } else {
    model.num <- cbind(model.num, paste("Model", r))
    ftext.model <- cbind(ftext.model, ftext.model.r)
    ftext.hcode <- cbind(ftext.hcode, ftext.hcode.r)
    ftext.ftype <- cbind(ftext.ftype, ftext.ftype.r)
    ftext.version <- cbind(ftext.version, ftext.version.r)
    ftext.id <- cbind(ftext.id, ftext.id.r)
    
    model.comparison <- rbind(ftext.model,ftext.hcode, ftext.ftype,
                              ftext.version, ftext.id)
    colnames(model.comparison) <- c(model.num)
    rownames(model.comparison) <- c("Model", "Hydrocode", "Ftype", "Model Version", 
                                    "Run ID")
    title_param <- paste(title_param, "vs", paste(ftext.model.r))
  }
}

model.info <- model.comparison %>% as.data.frame() %>% add_rownames() %>% qflextable()

# Set column widths
model.info <- width(model.info, j = 2:length(model.comparison[1,]), width = 1.9)
model.info <- width(model.info, j = 1, width = 2.5)

# Set theme
model.info <- theme_box(model.info)

# Set background color of select rows --------------------------------------------------------------
model.info <- bg(model.info, bg = "#EFEFEF", part = "header")
model.info <- set_header_labels(model.info, rowname = "Properties")
fontsize(model.info, size = 9)
}

```

```{r LoadStatsTable, include=FALSE}
rseg_table <- rseg_metrics.df
rseg_table <- cbind(rownames(rseg_table),rseg_table)
names(rseg_table)[names(rseg_table) == 'rownames(rseg_table)'] <- 'Desc'
rseg_table_raw <- rseg_table

rseg_table_sql <- paste('SELECT
                  CASE
                    WHEN "Desc" = "model" THEN "River Segment Model Statistics:"
                    WHEN "Desc" = "Qout" THEN "Mean Flow Out (cfs)"
                    WHEN "Desc" = "Qbaseline" THEN "Baseline Flow (cfs)"
                    WHEN "Desc" = "remaining_days_p0" THEN "Minimum Days of Storage Remaining"
                    WHEN "Desc" = "l01_Qout" THEN "1 Day Low Flow (cfs)"
                    WHEN "Desc" = "l07_Qout" THEN "7 Day Low Flow (cfs)"
                    WHEN "Desc" = "l30_Qout" THEN "30 Day Low Flow (cfs)"
                    WHEN "Desc" = "l90_Qout" THEN "90 Day Low Flow (cfs)"
                    WHEN "Desc" = "consumptive_use_frac" THEN "Consumptive Use Fraction (1.0-Qout/Qbaseline)"
                    WHEN "Desc" = "wd_cumulative_mgd" THEN "Cumulative Withdrawal Flow Out (mgd)"
                    WHEN "Desc" = "ps_cumulative_mgd" THEN "Cumulative Point Source Flow In (mgd)"
                    WHEN "Desc" = "wd_mgd" THEN "Withdrawal Flow Out (mgd)"
                    WHEN "Desc" = "ps_mgd" THEN "Point Source Flow In (mgd)"
                    ELSE Desc
                  END AS Description, *
                 FROM rseg_table_raw
                 WHERE Desc NOT IN ("riverseg","run_date","starttime","endtime","richness_change_abs","richness_change_pct","runid")
                 ',sep='')
rseg_table <- sqldf(rseg_table_sql)
rseg_table <- rseg_table[,-2]
#-------------------------------------------------------------------------------
statsdf <- rbind(rseg_table)
```

\newpage
# Flow Modeling

## Flow Duration Curve
```{r FDCRetrieve, echo = FALSE, message = FALSE, results = "asis", fig.cap=paste("Flow duration curves from VAHydro:", title_param), fig.id = "fdc", fig.cap.style = "Image Caption"}
for (r in 1:length(rseg.model.version)) {
  runid.r <- runid.list[r]
  rseg.runid.r <- dat[[r]][[runid.r]]
  path.fdc.r <- rseg.runid.r[['fig.fdc']][['code']]

  if (r == 1) {
    fig.fdc <- paste0("![](",path.fdc.r,")")
  } else {
    fig.fdc <- paste(paste0(fig.fdc,"{width=1/",r,"}"), paste0("![](",path.fdc.r,")","{width=1/",r,"}"))
  }
}

cat(fig.fdc)
```

## Mean Flow, Withdrawals and Point Sources
```{r AllFlowsRetrieve, echo = FALSE, message = FALSE, results = "asis", fig.cap=paste("Discharge, point sources, and withdrawals from VAHydro:", title_param), fig.id = "all_flows", fig.cap.style = "Image Caption"}
for (r in 1:length(rseg.model.version)) {
  runid.r <- runid.list[r]
  rseg.runid.r <- dat[[r]][[runid.r]]
  path.flows.all.r <- rseg.runid.r[['fig.flows.all']][['code']]
  
  # if (r == 1){
  #   fig.flows.all <- ggdraw() + 
  #     draw_image(path.flows.all.r)
  # } else {
  #   fig.flows.all.r <- ggdraw() +
  #     draw_image(path.flows.all.r)
  #   fig.flows.all <- list(fig.flows.all, fig.flows.all.r)
  # }
  
  if (r == 1) {
    fig.flows.all <- paste0("![](",path.flows.all.r,")")
  } else {
    fig.flows.all <- paste(paste0(fig.flows.all,"{width=1/",r,"}"), paste0("![](",path.flows.all.r,")","{width=1/",r,"}"))
  }
  
  # if (r == 1) {
  #   fig.flows.all
  # } else {
  #   do.call("grid.arrange", c(fig.flows.all, ncol = r)) 
  # }
}
cat(fig.flows.all)
```

## Dry Period Hydrograph
```{r DryRetrieve, echo = FALSE, message = FALSE, results = "asis", fig.cap=paste("The dry periods from VAHydro:", title_param), fig.id = "dry_periods", fig.cap.style = "Image Caption"}
for (r in 1:length(rseg.model.version)) {
  runid.r <- runid.list[r]
  rseg.runid.r <- dat[[r]][[runid.r]]
  path.hydrograph.dry.r <- rseg.runid.r[['fig.hydrograph_dry']][['code']]

 # if (r == 1){
 #    fig.hydrograph.dry <- ggdraw() + 
 #      draw_image(path.hydrograph.dry.r)
 #  } else {
 #    fig.hydrograph.dry.r <- ggdraw() +
 #      draw_image(path.hydrograph.dry.r)
 #    fig.hydrograph.dry <- list(fig.hydrograph.dry, fig.hydrograph.dry.r)
 #  }
  
  if (r == 1) {
    fig.hydrograph.dry <- paste0("![](",path.hydrograph.dry.r,")")
  } else {
    fig.hydrograph.dry <- paste(paste0(fig.hydrograph.dry,"{width=1/",r,"}"),
                                paste0("![](",path.hydrograph.dry.r,")","{width=1/",r,"}"))
  }
  
  # if (r == 1) {
  #   fig.hydrograph.dry
  # } else {
  #   do.call("grid.arrange", c(fig.hydrograph.dry, ncol = r)) 
  # }
}
cat(fig.hydrograph.dry)
```

## 90-day Low Flows over a 2 year Period
```{r L902YRetrieve, echo = FALSE, message = FALSE, results = "asis", fig.cap=paste("The 2 year, 90-day low flows from VAHydro:", title_param), fig.id = "2yr_l90", fig.cap.style = "Image Caption"}
for (r in 1:length(rseg.model.version)) {
  runid.r <- runid.list[r]
  rseg.runid.r <- dat[[r]][[runid.r]]
  path.l90.2yr.r <- rseg.runid.r[['fig.l90_flows.2yr']][['code']]
  
  # if (r == 1){
  #   fig.l90.2yr <- ggdraw() + 
  #     draw_image(path.l90.2yr.r)
  # } else {
  #   fig.l90.2yr.r <- ggdraw() +
  #     draw_image(path.l90.2yr.r)
  #   fig.l90.2yr <- list(fig.l90.2yr, fig.l90.2yr.r)
  # }
  
  if (r == 1) {
    fig.l90.2yr <- paste0("![](",path.l90.2yr.r,")")
  } else {
    fig.l90.2yr <- paste(paste0(fig.l90.2yr,"{width=1/",r,"}"), paste0("![](",path.l90.2yr.r,")","{width=1/",r,"}"))
  }
  
  # if (r == 1) {
  #   fig.l90.2yr
  # } else {
  #   do.call("grid.arrange", c(fig.l90.2yr, ncol = r)) 
  # }
}
cat(fig.l90.2yr)
```

## Ftable Visual
```{r ftable_crosssection, echo=FALSE}
#get ftable:
path_uci <- 'http://deq1.bse.vt.edu:81/p6/vadeq/input/param/river/vahydro_2022/ftables/'

ftable_raw <- read.csv(paste(path_uci, rseg.hydrocode[1], '.ftable', sep=''), 
                    sep='', 
                    header=FALSE)

#remove flow-thru col if it exists (for old models):
if (ncol(ftable_raw)>4) {
  ftable_raw <- ftable_raw[,1:4]
}
#rename columns:
colnames(ftable_raw) <- c('depth','area','vol','disch')

#remove the row w/ matrix dimensions of the data (typically it's: [19,4] )
dimensions_data <- as.numeric(rownames(ftable_raw[grep('ROWS', ftable_raw[, 1]),])) + 1 #add 1 because dimensions are 1 row below "ROWS COLS ***" comment/header row
ftable_raw <- ftable_raw[-dimensions_data,]
rownames(ftable_raw) <- seq(1, length(ftable_raw$depth)) #fix row numbers; otherwise we lose data in the for-loop

#create empty data frame to add rows we're keeping (otherwise row numbers get scrambled in the for-loop):
ftable <- data.frame(matrix(nrow=0, ncol=4))
colnames(ftable) <- c('depth','area','vol','disch')

for (i in 1:length(ftable_raw$depth)) {
  if (!is.na(as.numeric(ftable_raw$depth[i]))) {
    #only keep numeric data
    row_i <- as.numeric(rownames(ftable_raw[i,]))
    ftable <- rbind(ftable, ftable_raw[row_i,])
  }
}
rownames(ftable) <- seq(1, length(ftable$depth)) #fix row numbers for clarity

#pull channel length:
rseg<- RomFeature$new(ds,list(
    hydrocode= rseg.hydrocode[2], 
    ftype= rseg.ftype[2],
    bundle='watershed'), 
    TRUE)
model <- RomProperty$new(ds,list(
    varkey="om_water_model_node",
    featureid=rseg$hydroid,
    entity_type="dh_feature", 
    propcode=rseg.model.version[2]), 
  TRUE)
channel_prop <- RomProperty$new(ds,list(
    #varkey="om_USGSChannelGeomObject", #for local_channel it needs _sub added to end
    featureid=model$pid,
    entity_type='dh_properties',
    propname = '0. River Channel'),
  TRUE)
length <- RomProperty$new(channel_prop[["datasource"]],list(
    varkey="om_class_Constant",
    featureid=channel_prop$pid,
    entity_type='dh_properties',
    propname='length'),
  TRUE)
clength <- length$propvalue #channel length in ft

#generate 3D coordinates:
ftable$x <- ftable$area*43560/clength/2 #divide by 2 to get 1/2 the surface width (middle of plot is x=0 -> sw is -x to x)
#multiply by 43560 to go acres --> sqft

x <- c(ftable$x[-1], -ftable$x[-1]) #make sure there aren't 2 rows where x=0
y <- seq(0, clength, length.out=length(x))
z <- c(ftable$depth[-1], ftable$depth[-1])

pair <- cbind(x, z)
pair <- pair[order(x),] #ascending order
x <- pair[,1]
z <- pair[,-1]

for (i in 1:(length(x)-1)){
  z <- cbind(z, pair[,-1])
}
colnames(z) <- y #to conceptualize data
rownames(z) <- x

#plot channel:
persp(x, y, z, theta = 5, phi = 15, expand = .2, col = "#0099CC", axes=TRUE, nticks=8, ticktype="detailed", scale=TRUE, shade=0.65, border="003300", d=0.6, r=9, xlab="Width (ft)",
      ylab="Channel Length (ft)", zlab="Depth (ft)", 
      main=paste(rseg.hydrocode[1], "FTABLE"),
      sub=paste("Water shown in channel at a depth of", ftable$depth[15],"ft \n Bankfull is approx.", ftable$depth[10], "ft"))->channel
  for(i in 1:15){
    lines (trans3d(x = c(-ftable$x[i], ftable$x[i]), y = seq(0, clength, by=10) , z = ftable$depth[i], pmat = channel), 
           col ="#33CCFF3F", pch=16) #bankfull
  }
#note: adding "_F" to the end of a color gives it transparency. 1 is more transparent; 9 is more opaque

persp(x, y, z, theta = 10, phi = 15, expand = .2, col = "#0099CC", axes=TRUE, nticks=8, ticktype="detailed", scale=TRUE, shade=0.65, border="003300", d=0.6, r=9, xlab="Width (ft)", ylab="Channel Length (ft)", zlab="Depth (ft)", main=paste(rseg.hydrocode[1], "FTABLE"), sub=paste("Bankfull Depth is approx.", ftable$depth[10], "ft"))

persp(x, y, z, theta = -5, phi = -15, expand = .2, col = "#0099CC", axes=TRUE, nticks=8, ticktype="detailed", scale=TRUE, shade=0.65, border="003300", d=0.6, r=9, xlab="Width (ft)", ylab="Channel Length (ft)", zlab="Depth (ft)", main=paste(rseg.hydrocode[1], "FTABLE"), sub=paste("Bankfull Depth is approx.", ftable$depth[10], "ft"))

```

\newpage
# Time Series Analysis

```{r MathcingData, echo = FALSE}
# retrieving and matching the data

for (r in 1:length(rseg.model.version)) {
  rseg.data.r <- data.table::fread(rseg.file.path[r])
  assign(paste0('rseg.data.',r),rseg.data.r)
  rseg.cols.r <- names(rseg.data.r)

   if (r == 1){
      data.match <- rseg.data.r$date
      sdate <- as.Date(min(data.match))
      edate <- as.Date(max(data.match))
    } else {
      data.match <- match(data.match, rseg.data.r$date)
      sdate <- as.Date(min(data.match))
      edate <- as.Date(max(data.match))
    }
}

for (r in 1:length(rseg.model.version)) {
  rseg.flow.r <- zoo(as.numeric(as.character(rseg.data.r$Qout)), order.by = rseg.data.r$index)
  rseg.flow.r <- window(rseg.flow.r, start = sdate, end = edate)
  mode(rseg.flow.r) <- 'numeric'

  assign(paste0('rseg.flow.',r),rseg.flow.r)
}

# generate low flow data
for (r in 1:length(rseg.model.version)) {
  rseg.lowflow.r <- IHA::group2(rseg.flow.r)
  assign(paste0('rseg.lowflow.',r),rseg.lowflow.r)
}
```

## 90-Day Low Flow Comparison
```{r 90day, echo = FALSE, fig.cap=paste("The 90-day low flows:", title_param), fig.id = "90day", fig.cap.style = "Image Caption"}
for (r in 1:length(rseg.model.version)) {
  if (r == 1) {
    l90.data <- data.frame(rseg.lowflow.r$year, rseg.lowflow.r["90 Day Min"])
    colname.l90 <- paste0(rseg_model_info.r[[1]][[3]])
  } else {
    l90.data <- cbind(l90.data, rseg.lowflow.r["90 Day Min"])
    colnames(l90.data) <- c("Year", colname.l90, paste0(rseg_model_info.r[[1]][[3]]))
    ymax.l90 <- max(l90.data[-1])
  }
}

values.l90 <- tidyr::pivot_longer(l90.data, -Year, names_to="Model", values_to="Flow")
l90.plot <- ggplot(values.l90, aes(y=Flow, x=Year, fill = Model)) + 
    geom_bar(position="dodge", stat="identity", color="darkgrey") +
    theme_light() +
    theme(legend.title = element_text(size=10),
          legend.text = element_text(size=10),
          legend.position = "top",
          legend.key.size = unit(0.25,"cm")) +
    ylab("Flow (cfs)") +
    scale_fill_brewer()
l90.plot
```

## 30-Day Low Flow Comparison
```{r 30day, echo = FALSE, fig.cap=paste("The 30-day low flows:", title_param), fig.id = "30day", fig.cap.style = "Image Caption"}
for (r in 1:length(rseg.model.version)) {
  if (r == 1) {
    l30.data <- data.frame(rseg.lowflow.r$year, rseg.lowflow.r["90 Day Min"])
    colname.l30 <- paste0(rseg_model_info.r[[1]][[3]])
  } else {
    l30.data <- cbind(l30.data, rseg.lowflow.r["90 Day Min"])
    colnames(l30.data) <- c("Year", colname.l30, paste0(rseg_model_info.r[[1]][[3]]))
    ymax.l30 <- max(l30.data[-1])
  }
}

values.l30 <- tidyr::pivot_longer(l30.data, -Year, names_to="Model", values_to="Flow")
l30.plot <- ggplot(values.l30, aes(y=Flow, x=Year, fill = Model)) + 
    geom_bar(position="dodge", stat="identity", color="darkgrey") +
    theme_light() +
    theme(legend.title = element_text(size=10),
          legend.text = element_text(size=10),
          legend.position = "top",
          legend.key.size = unit(0.25,"cm")) +
    ylab("Flow (cfs)") +
    scale_fill_brewer()
l30.plot
```

## 7-Day Low Flow Comparison
```{r 7day, echo = FALSE, fig.cap=paste("The 7-day low flows:", title_param), fig.id = "7day", fig.cap.style = "Image Caption"}
for (r in 1:length(rseg.model.version)) {
  if (r == 1) {
    l7.data <- data.frame(rseg.lowflow.r$year, rseg.lowflow.r["90 Day Min"])
    colname.l7 <- paste0(rseg_model_info.r[[1]][[3]])
  } else {
    l7.data <- cbind(l7.data, rseg.lowflow.r["90 Day Min"])
    colnames(l7.data) <- c("Year", colname.l7, paste0(rseg_model_info.r[[1]][[3]]))
    ymax.l7 <- max(l7.data[-1])
  }
}

values.l7 <- tidyr::pivot_longer(l7.data, -Year, names_to="Model", values_to="Flow")
l7.plot <- ggplot(values.l7, aes(y=Flow, x=Year, fill = Model)) + 
    geom_bar(position="dodge", stat="identity", color="darkgrey") +
    theme_light() +
    theme(legend.title = element_text(size=10),
          legend.text = element_text(size=10),
          legend.position = "top",
          legend.key.size = unit(0.25,"cm")) +
    ylab("Flow (cfs)") +
    scale_fill_brewer()
l7.plot
```

## 1-Day Low Flow Comparison
```{r 1day, echo = FALSE, fig.cap=paste("The 1-day low flows:", title_param), fig.id = "1day", fig.cap.style = "Image Caption"}
for (r in 1:length(rseg.model.version)) {
  if (r == 1) {
    l1.data <- data.frame(rseg.lowflow.r$year, rseg.lowflow.r["90 Day Min"])
    colname.l1 <- paste0(rseg_model_info.r[[1]][[3]])
  } else {
    l1.data <- cbind(l1.data, rseg.lowflow.r["90 Day Min"])
    colnames(l1.data) <- c("Year", colname.l1, paste0(rseg_model_info.r[[1]][[3]]))
    ymax.l1 <- max(l1.data[-1])
  }
}

values.l1 <- tidyr::pivot_longer(l1.data, -Year, names_to="Model", values_to="Flow")
geom_bar(position="dodge", stat="identity", color="darkgrey") +
    theme_light() +
    theme(legend.title = element_text(size=10),
          legend.text = element_text(size=10),
          legend.position = "top",
          legend.key.size = unit(0.25,"cm")) +
    ylab("Flow (cfs)") +
    scale_fill_brewer()
l1.plot
```

## Model Performance Scatterplots

``` {r scatter, echo = FALSE, fig.cap=paste("The low flow scenarios and differences between:", title_param), fig.id = "scatter1", fig.cap.style = "Image Caption"}

if (length(rseg.model.version) == 2) {

  l90.scatter <- ggplot(l90.data, aes(x = get(names(l90.data)[2]), y = get(names(l90.data)[3]))) +
  geom_point() +
  geom_smooth(method=lm) +
  theme_light() +
  theme(axis.title.x = element_text(size = 9),
        axis.title.y = element_text(size = 9)) +
  ylab(colnames(l90.data[2])) +
  xlab(colnames(l90.data[3]))

  # L90 Error Scatterplot
  l90_diff <- unlist(l90.data[2] - l90.data[3]) # has to unlist in order to plot with ggplot!
  l90_diff_pct <- 100.0 * (l90_diff) / l90.data[3]
  
  l90.diff <- ggplot(l90.data, aes(x =get(names(l90.data)[1]), y = l90_diff)) +
    geom_point() +
    geom_smooth(method=lm) +
    theme_light() +
    theme(axis.title.x = element_text(size = 9),
          axis.title.y = element_text(size = 9)) +
    ylab(paste("Difference: Model 1 - Model 2")) +
    xlab(paste("Year"))
  
  l30.scatter <- ggplot(l30.data, aes(x = get(names(l30.data)[2]), y = get(names(l30.data)[3]))) +
    geom_point() +
    geom_smooth(method=lm) +
    theme_light() +
    theme(axis.title.x = element_text(size = 9),
          axis.title.y = element_text(size = 9)) +
    ylab(colnames(l30.data[2])) +
    xlab(colnames(l30.data[3]))
  
  # l30 Error Scatterplot
  l30_diff <- unlist(l30.data[2] - l30.data[3]) # has to unlist in order to plot with ggplot!
  l30_diff_pct <- 100.0 * (l30_diff) / l30.data[3]
  
  l30.diff <- ggplot(l30.data, aes(x =get(names(l30.data)[1]), y = l30_diff)) +
    geom_point() +
    geom_smooth(method=lm) +
    theme_light() +
    theme(axis.title.x = element_text(size = 9),
          axis.title.y = element_text(size = 9)) +
    ylab(paste("Difference: Model 1 - Model 2")) +
    xlab(paste("Year"))
  
  l7.scatter <- ggplot(l7.data, aes(x = get(names(l7.data)[2]), y = get(names(l7.data)[3]))) +
    geom_point() +
    geom_smooth(method=lm) +
    theme_light() +
    theme(axis.title.x = element_text(size = 9),
          axis.title.y = element_text(size = 9)) +
    ylab(colnames(l7.data[2])) +
    xlab(colnames(l7.data[3]))
  
  # l7 Error Scatterplot
  l7_diff <- unlist(l7.data[2] - l7.data[3]) # has to unlist in order to plot with ggplot!
  l7_diff_pct <- 100.0 * (l7_diff) / l7.data[3]
  
  l7.diff <- ggplot(l7.data, aes(x =get(names(l7.data)[1]), y = l7_diff)) +
    geom_point() +
    geom_smooth(method=lm) +
    theme_light() +
    theme(axis.title.x = element_text(size = 9),
          axis.title.y = element_text(size = 9)) +
    ylab(paste("Difference: Model 1 - Model 2")) +
    xlab(paste("Year"))

  l1.scatter <- ggplot(l1.data, aes(x = get(names(l1.data)[2]), y = get(names(l1.data)[3]))) +
    geom_point() +
    geom_smooth(method=lm) +
    theme_light() +
    theme(axis.title.x = element_text(size = 9),
          axis.title.y = element_text(size = 9)) +
    ylab(colnames(l1.data[2])) +
    xlab(colnames(l1.data[3]))
  
  # l1 Error Scatterplot
  l1_diff <- unlist(l1.data[2] - l1.data[3]) # has to unlist in order to plot with ggplot!
  l1_diff_pct <- 100.0 * (l1_diff) / l1.data[3]
  
  l1.diff <- ggplot(l1.data, aes(x =get(names(l1.data)[1]), y = l1_diff)) +
    geom_point() +
    geom_smooth(method=lm) +
    theme_light() +
    theme(axis.title.x = element_text(size = 9),
          axis.title.y = element_text(size = 9)) +
    ylab(paste("Difference: Model 1 - Model 2")) +
    xlab(paste("Year"))
  
  plots <- align_plots(l90.scatter, l1.scatter, align = 'v', axis = 'l')
  plot_row1 <- plot_grid(plots[[1]], l90.diff , 
                         labels = c("90 Day Low Flow" ," "), label_size = 10,
                         rel_widths = c(0.5, 0.5), rel_heights = c(0.5,0.5))
  plot_row2 <- plot_grid(l30.scatter, l30.diff, 
                         labels = c("30 Day Low Flow" ," "), label_size = 10,
                         rel_widths = c(0.5, 0.5))
  plot_row3 <- plot_grid(l7.scatter, l7.diff, 
                         labels = c("7 Day Low Flow" ," "), label_size = 10,
                         rel_widths = c(0.5, 0.5))
  plot_row4 <- plot_grid(plots[[2]], l1.diff, 
                         labels = c("1 Day Low Flow" ," "), label_size = 10,
                         rel_widths = c(0.5, 0.5))
  
  plot_grid(plot_row1, plot_row2, plot_row3, plot_row4, ncol = 1)
}
```

## Model %-Difference

``` {r percent, echo = FALSE}



```

\newpage
<!---BLOCK_LANDSCAPE_START--->
# Metrics Summary

```{r StatsTable, echo=FALSE}
ft <- qflextable(statsdf)

# Set column widths
ft <- width(ft, j = 2:length(statsdf[1,]), width = 1.9)
ft <- width(ft, j = 1, width = 2.5)

# Set theme
ft <- theme_box(ft)

# Set background color of select rows --------------------------------------------------------------
ft <- bg(ft, bg = "#EFEFEF", part = "header")
ft <- bg(ft, i = ~ Description == "River Segment Model Statistics:", bg = "#EFEFEF", part = "body")
fontsize(ft, size = 9)
```
<!---BLOCK_LANDSCAPE_STOP--->

\newpage
