---
date: "`r format(Sys.time(), '%m/%d/%Y')`"
author: ""
title: "`r params$doc_title`"
output: 
  officedown::rdocx_document:
    mapstyles:
      Normal: ['First Paragraph']
    page_margins:
      bottom: 0.5
      top: 0.5
      right: 1
      left: 0.5
      header: 0.0
      footer: 0.0
params: 
  doc_title: "Comparison of Two VaHydro Models"
  rseg.file.path: [ "/media/model/p6/out/river/hsp2_2022/hydr/JA4_7280_7340_hydrd_wy.csv", "/media/model/p6/out/river/subsheds/hydr/JA4_7280_7340_hydrd_wy.csv" ]
  rseg.hydrocode: [ "JA4_7280_7340","vahydrosw_wshed_JA4_7280_7340" ]
  rseg.ftype: [ "cbp60","vahydro" ]
  rseg.model.version: [ "cbp-6.0","cbp-6.1" ]
  runid.list: [ "hsp2_2022","subsheds" ]
  rseg.metric.list: [ "Qout","l90_Qout","l30_Qout","l07_Qout","l01_Qout","consumptive_use_frac","wd_cumulative_mgd","ps_cumulative_mgd","wd_mgd","ps_mgd" ]
---

```{r setup, include=FALSE}
#https://cran.r-project.org/web/packages/officedown/officedown.pdf
#https://ardata-fr.github.io/officeverse/officedown-for-word.html#insert-sections
knitr::opts_chunk$set(echo = TRUE, fig.cap = TRUE)
library(officedown)
library(officer)
library(flextable)
library(hydrotools)
library(rjson)
library(cowplot)
library(gridExtra)
library(grid)
library(png)
library(tidyr)
library(ggplot2)
library(dplyr)
library(data.table)
basepath='/var/www/R'
source('/var/www/R/config.R')

site <- 'http://deq1.bse.vt.edu/d.dh'
esite <- 'http://deq1.bse.vt.edu:81'
json_obj_url <- paste(site, "node/62", sep ="/")

ds <- RomDataSource$new("http://deq1.bse.vt.edu/d.dh", rest_uname)
ds$get_token(rest_pw)
# Load functions used during development
source("https://raw.githubusercontent.com/HARPgroup/hydro-tools/master/VAHydro-2.0/fn_get_prop.R")
source("https://raw.githubusercontent.com/HARPgroup/hydro-tools/master/VAHydro-2.0/rest_functions.R")
source("https://raw.githubusercontent.com/HARPgroup/hydro-tools/master/VAHydro-2.0/find_name.R")

fp <- fp_par(
  text.align = "center", 
  padding.bottom = 20, padding.top = 120, 
  border.bottom = fp_border())

ft <- fp_text(shading.color='#EFEFEF', bold = TRUE)

```

# Table of contents
```{r, echo = FALSE}
block_toc()
```

```{r UserInputs, include=FALSE}
rseg.filepath <- params$rseg.file.path
rseg.hydrocode <- params$rseg.hydrocode
rseg.ftype <- params$rseg.ftype
rseg.model.version <- params$rseg.model.version
runid.list <- params$runid.list
rseg.metric.list <- params$rseg.metric.list

rlist <- gsub('runid_', '', runid.list)

# r <- 1
for (r in 1:length(rseg.model.version)){
  
  # get rseg feature
  rseg.hydrocode.r <- rseg.hydrocode[r]
  rseg.ftype.r <- rseg.ftype[r]
  rseg_feature <- RomFeature$new(
    ds,
    list(hydrocode = rseg.hydrocode.r, ftype = rseg.ftype.r),
    TRUE
  )
  rseg.hydroid.r <- rseg_feature$hydroid
  
  # get rseg model
  rseg.model.version.r <- rseg.model.version[r]
  print(paste("searching", rseg.model.version.r,"model for river segment hydroid", rseg.hydroid.r))
  rseg.model.r <- RomProperty$new(
    ds,
    list(entity_type='dh_feature', featureid = rseg.hydroid.r, propcode=rseg.model.version.r),
    TRUE
  )
  
  if (exists("json_obj_url")) {
  rseg_obj_url.r <- paste(json_obj_url, rseg.model.r$pid, sep="/")
  rseg_model_info.r <- ds$auth_read(rseg_obj_url.r, "text/json", "")
  rseg_model_info.r <- fromJSON(rseg_model_info.r)
  } else {
  message("Error: json_obj_url is undefined.  Can not retrieve model and scenario information. (Hint: Use config.R
          to set json_obj_url) ")
  rseg_model_info.r <- list()
  }
  
  # stash the model run data into a combined list
  if (r == 1){
    dat <- rseg_model_info.r
  } else {
    dat <- cbind(dat,rseg_model_info.r)
  }
  
  # retrieve metrics for a run
  runid.r <- runid.list[r]
  rseg_table.r <- om_model_table(model_info = rseg_model_info.r,
                             runid.list = runid.r,
                             metric.list = rseg.metric.list,
                             include.elfgen = TRUE,
                             site = site,
                             site_base = omsite
                             )

  # join results from multiple runs to a single dataframe & create captioning for later
  if (r == 1){
    rseg_metrics.df <- rseg_table.r
  } else {
    rseg_metrics.df <- cbind(rseg_metrics.df,rseg_table.r)
  }

}

```

The models compared in this document are:
``` {r modelinfo, echo = FALSE, tab.cap = 'Properties of each model compared in this document.', tab.id="modelinfo"}
for (r in 1:length(rseg.model.version)){
  ftext.model.r <- paste(dat[[r]][[3]])
  ftext.hcode.r <- paste(rseg.hydrocode[r])
  ftext.ftype.r <- paste(rseg.ftype[r])
  ftext.version.r <- paste(rseg.model.version[r])
  ftext.id.r <- paste(runid.list[r])
  
  if (r == 1){
    model.num <- paste("Model", r)
    ftext.model <- ftext.model.r 
    ftext.hcode <- ftext.hcode.r 
    ftext.ftype <- ftext.ftype.r 
    ftext.version <- ftext.version.r 
    ftext.id <- ftext.id.r
    title_param <- paste(ftext.model.r)
  } else {
    model.num <- cbind(model.num, paste("Model", r))
    ftext.model <- cbind(ftext.model, ftext.model.r)
    ftext.hcode <- cbind(ftext.hcode, ftext.hcode.r)
    ftext.ftype <- cbind(ftext.ftype, ftext.ftype.r)
    ftext.version <- cbind(ftext.version, ftext.version.r)
    ftext.id <- cbind(ftext.id, ftext.id.r)
    
    model.comparison <- rbind(ftext.model,ftext.hcode, ftext.ftype,
                              ftext.version, ftext.id)
    colnames(model.comparison) <- c(model.num)
    rownames(model.comparison) <- c("Model", "Hydrocode", "Ftype", "Model Version", 
                                    "Run ID")
    title_param <- paste(title_param, "vs", paste(ftext.model.r))
  }
}

model.info <- model.comparison %>% as.data.frame() %>% add_rownames() %>% qflextable()

# Set column widths
model.info <- width(model.info, j = 2:length(model.comparison[1,]), width = 1.9)
model.info <- width(model.info, j = 1, width = 2.5)

# Set theme
model.info <- theme_box(model.info)

# Set background color of select rows --------------------------------------------------------------
model.info <- bg(model.info, bg = "#EFEFEF", part = "header")
model.info <- set_header_labels(model.info, rowname = "Properties")
fontsize(model.info, size = 9)

```

```{r LoadStatsTable, include=FALSE}
rseg_table <- rseg_metrics.df
rseg_table <- cbind(rownames(rseg_table),rseg_table)
names(rseg_table)[names(rseg_table) == 'rownames(rseg_table)'] <- 'Desc'
rseg_table_raw <- rseg_table

rseg_table_sql <- paste('SELECT
                  CASE
                    WHEN "Desc" = "model" THEN "River Segment Model Statistics:"
                    WHEN "Desc" = "Qout" THEN "Mean Flow Out (cfs)"
                    WHEN "Desc" = "Qbaseline" THEN "Baseline Flow (cfs)"
                    WHEN "Desc" = "remaining_days_p0" THEN "Minimum Days of Storage Remaining"
                    WHEN "Desc" = "l01_Qout" THEN "1 Day Low Flow (cfs)"
                    WHEN "Desc" = "l07_Qout" THEN "7 Day Low Flow (cfs)"
                    WHEN "Desc" = "l30_Qout" THEN "30 Day Low Flow (cfs)"
                    WHEN "Desc" = "l90_Qout" THEN "90 Day Low Flow (cfs)"
                    WHEN "Desc" = "consumptive_use_frac" THEN "Consumptive Use Fraction (1.0-Qout/Qbaseline)"
                    WHEN "Desc" = "wd_cumulative_mgd" THEN "Cumulative Withdrawal Flow Out (mgd)"
                    WHEN "Desc" = "ps_cumulative_mgd" THEN "Cumulative Point Source Flow In (mgd)"
                    WHEN "Desc" = "wd_mgd" THEN "Withdrawal Flow Out (mgd)"
                    WHEN "Desc" = "ps_mgd" THEN "Point Source Flow In (mgd)"
                    ELSE Desc
                  END AS Description, *
                 FROM rseg_table_raw
                 WHERE Desc NOT IN ("riverseg","run_date","starttime","endtime","richness_change_abs","richness_change_pct","runid")
                 ',sep='')
rseg_table <- sqldf(rseg_table_sql)
rseg_table <- rseg_table[,-2]
#-------------------------------------------------------------------------------
statsdf <- rbind(rseg_table)
```


\newpage
# Flow Modeling

## Flow Duration Curve
```{r FDCRetrieve, echo = FALSE, message = FALSE, results = "asis", fig.cap=paste("Flow duration curves from VAHydro:", title_param), fig.id = "fdc", fig.cap.style = "Image Caption", out.width = '100%'}
for (r in 1:length(rseg.model.version)) {
  runid.r <- runid.list[r]
  rseg.runid.r <- dat[[r]][[runid.r]]
  path.fdc.r <- rseg.runid.r[['fig.fdc']][['code']]
  
  if (r == 1){
    fdc <- png::readPNG(getURLContent(path.fdc.r))
  } else {
    fdc.r <- png::readPNG(getURLContent(path.fdc.r))
    fdc <- list(rasterGrob(fdc), rasterGrob(fdc.r))
  }
  
  if (r == 1) {
    fdc
  } else {
    do.call("grid.arrange", c(fdc, ncol = r))
  }
}
```

## Mean Flow, Withdrawals and Point Sources
```{r AllFlowsRetrieve, echo = FALSE, message = FALSE, results = "asis", fig.cap=paste("Discharge, point sources, and withdrawals from VAHydro:", title_param), fig.id = "all_flows", fig.cap.style = "Image Caption", out.width = '100%'}
for (r in 1:length(rseg.model.version)) {
  runid.r <- runid.list[r]
  rseg.runid.r <- dat[[r]][[runid.r]]
  path.flows.all.r <- rseg.runid.r[['fig.flows.all']][['code']]
  
  if (r == 1){
    all.flows <- png::readPNG(getURLContent(path.flows.all.r))
  } else {
    all.flows.r <- png::readPNG(getURLContent(path.flows.all.r))
    all.flows <- list(rasterGrob(all.flows), rasterGrob(all.flows.r))
  }
  
  if (r == 1) {
    all.flows
  } else {
    do.call("grid.arrange", c(all.flows, ncol = r))
  }
}

```

## Dry Period Hydrograph
```{r DryRetrieve, echo = FALSE, message = FALSE, results = "asis", fig.cap=paste("The dry periods from VAHydro:", title_param), fig.id = "dry_periods", fig.cap.style = "Image Caption", out.width = '100%'}
for (r in 1:length(rseg.model.version)) {
  runid.r <- runid.list[r]
  rseg.runid.r <- dat[[r]][[runid.r]]
  path.hydrograph.dry.r <- rseg.runid.r[['fig.hydrograph_dry']][['code']]

   if (r == 1){
    hydrograph <- png::readPNG(getURLContent(path.hydrograph.dry.r))
  } else {
    hydrograph.r <- png::readPNG(getURLContent(path.hydrograph.dry.r))
    hydrograph <- list(rasterGrob(hydrograph), rasterGrob(hydrograph.r))
  }
  
  if (r == 1) {
    hydrograph
  } else {
    do.call("grid.arrange", c(hydrograph, ncol = r))
  }
}
```

## 90-day Low Flows over a 2 year Period
```{r L902YRetrieve, echo = FALSE, message = FALSE, results = "asis", fig.cap=paste("The 2 year, 90-day low flows from VAHydro:", title_param), fig.id = "2yr_l90", fig.cap.style = "Image Caption", out.width = '100%'}
for (r in 1:length(rseg.model.version)) {
  runid.r <- runid.list[r]
  rseg.runid.r <- dat[[r]][[runid.r]]
  path.l90.2yr.r <- rseg.runid.r[['fig.l90_flows.2yr']][['code']]
  
  if (r == 1){
    l90.2yr <- png::readPNG(getURLContent(path.l90.2yr.r))
  } else {
    l90.2yr.r <- png::readPNG(getURLContent(path.l90.2yr.r))
    l90.2yr <- list(rasterGrob(l90.2yr), rasterGrob(l90.2yr.r))
  }
  
  if (r == 1) {
    l90.2yr
  } else {
    do.call("grid.arrange", c(l90.2yr, ncol = r))
  }
}
```

## Ftable Visual
```{r ftable_crosssection, echo=FALSE}
#get ftable:
path_uci <- 'http://deq1.bse.vt.edu:81/p6/vadeq/input/param/river/vahydro_2022/ftables/'
ftable <- read.csv(paste(path_uci,  rseg.hydrocode[1], '.ftable', sep=''), 
                    sep='', 
                    header=FALSE,
                    nrows = 19, skip= 5)
if (ncol(ftable)==5) {
  ftable <- ftable[,1:4] #remove flow-thru col if it exists (for old models)
}
colnames(ftable) <- c('depth','area','vol','disch')

#pull channel length:
rseg<- RomFeature$new(ds,list(
    hydrocode= rseg.hydrocode[2], 
    ftype= rseg.ftype[2],
    bundle='watershed'), 
    TRUE)
model <- RomProperty$new(ds,list(
    varkey="om_water_model_node",
    featureid=rseg$hydroid,
    entity_type="dh_feature", 
    propcode=rseg.model.version[2]), 
  TRUE)
channel_prop <- RomProperty$new(ds,list(
    #varkey="om_USGSChannelGeomObject", #for local_channel it needs _sub added to end
    featureid=model$pid,
    entity_type='dh_properties',
    propname = '0. River Channel'),
  TRUE)
length <- RomProperty$new(channel_prop[["datasource"]],list(
    varkey="om_class_Constant",
    featureid=channel_prop$pid,
    entity_type='dh_properties',
    propname='length'),
  TRUE)
clength <- length$propvalue #channel length

#extract geometry:
h <- ftable$depth[10]
Ah <- ftable$area[10]
SWh <- ftable$area[10]*43560/clength
b <- Ah/h*2 - SWh
slope <- (SWh-b)/(2*h)
bf <- b + 2*slope*h

ftable$sw <- ftable$area*43560/clength
#ftable$crossA <- ftable$vol*43560/clength


#practicevalues from JL2_6850_6890:
#h <- 8.770787/100
#b <- 80.93515/100
#bf <- 136.3575/100
#z <- 3.159484/100
#cslope <- 0.002241783/100
```

```{r, echo=FALSE}
# Generate data for the plot
fp <- 2.5*bf + 3/2*(bf-b)
trapezoid <- function(x, z){ #piecewise function utilizing R's understanding of TRUE==1 and FALSE==0
  (x>=-0.5*b & x<=0.5*b) * 0
  (x<=-0.5*bf & x>=-2.5*bf | x>=0.5*bf & x<=2.5*bf) * h +
  (x<=-fp| x>=fp) * (4*h) 
}

water <- function(x,z){
  #(x<=-0.5*bf & x>=-2.5*bf | x>=0.5*bf & x<=2.5*bf) * h/2
  (x<=-2.5*bf & x>=-fp) * (-slope*x + (h-2.5*slope*bf)) +
  (x>=2.5*bf & x<=fp) * (slope*x + (h-2.5*slope*bf))
}

x <- seq(-4*bf, 4*bf,length.out=50)
y <- seq(0, clength, length.out=50)
z <- outer(x, y, trapezoid)
z2 <- outer(x, y, water)

#fill <- matrix("lightblue", nr = nrow(z)-1, nc = ncol(z)-1)
#fill[,1] <- "gray"
#fill[,ncol(fill)] <- "gray"
#fill[1,] <- "gray"
#fill[nrow(fill),] <- "gray"

values<- cbind(x,y,z2)

# Create the plot
persp(x, y, z, theta = 10, phi = 20, expand = 0.1, col = "lightblue", axes=TRUE, nticks=10, ticktype="detailed", scale=TRUE)

persp(x, y, z2, theta = 10, phi = 20, expand = 0.1, col = "lightblue", axes=TRUE, nticks=10, ticktype="detailed", scale=TRUE)
```

```{r, echo=FALSE}
ftable$x <- rep(0,19)
for (i in 2:19){
 #print(ftable[i,])
 ftable$x[i] <- ftable$sw[i]/2
}

coord <- cbind(0,0)
colnames(coord) <- c("x","z")
for (i in 2:19){
  xcoord <- seq(-ftable$x[i], ftable$x[i], length.out=10)
  zcoord <- rep(ftable$depth[i], length(xcoord))
  pair <- cbind(xcoord, zcoord)
  coord <- rbind(coord, pair)
}
#persp(x, y, z, theta = 10, phi = 20, expand = 0.1, col = "lightblue", axes=TRUE, nticks=10, ticktype="detailed", scale=TRUE)
```

```{r, echo=FALSE}
# Visualizing a simple DEM model
z <- 2 * volcano     # Exaggerate the relief
x <- 10 * (1:nrow(z)) # 10 meter spacing (S to N)
y <- 10 * (1:ncol(z)) # 10 meter spacing (E to W)

# Don't draw the grid lines : border = NA
par(bg = "gray")
persp(x, y, z, theta = 135, phi = 30,
      col = "brown", scale = FALSE,
    ltheta = -120, shade = 0.75,
      border = NA, box = FALSE)
```

```{r, echo=TRUE}
x <- c(ftable$x, -ftable$x[-1]) #make sure there aren't 2 rows where x=0
y <- seq(0, clength, length.out=length(x))
z <- c(ftable$depth,ftable$depth)

pair <- cbind(x, z)
pair <- pair[order(x),] #ascending order
x <- pair[,1]
z <- pair[,-1]

for (i in 1:(length(x)-1)){
  z <- cbind(z, pair[,-1])
}
colnames(z) <- y #to conceptualize data
rownames(z) <- x

persp(x, y, z, theta = -10, phi = 15, expand = .2, col = "lightblue", axes=TRUE, nticks=8, ticktype="detailed", scale=TRUE, shade=0.75, border=NA, d=0.6, r=4.5)
```

```{r crosssect, echo=TRUE}
plot.new()
polygon(c(0, 0, 1, 1), c(0, 1, 1, 0))
polygon(c(0, 0.15, 0.23, 0.08), c(0.5, 0.9, 0.8, 0.4)) #left fp
polygon(c(0.08, 0.23, 0.36, 0.21), c(0.4, 0.8, 0.79, 0.39)) #left fp
polygon(c(0.645, 0.795, 0.926, 0.776), c(0.38, 0.784, 0.795, 0.4)) #rt fp
polygon(c(0.776, 0.846, 0.996, 0.926), c(0.4, 0.5, 0.895, 0.795)) #rt fp

segments(0.21, 0.39, 0.33, 0.15) #left channel
polygon(c(0.22, 0.33, 0.55, 0.635), c(0.37, 0.15, 0.14, 0.36), col='blue')
segments(0.55, 0.15, 0.645, 0.38) #rt channel

polygon(c(0.22, 0.635, 0.785, 0.365), c(0.37, 0.36, 0.76, 0.77), col='blue')
```

\newpage
# Time Series Analysis

```{r MathcingData, echo = FALSE}
# retrieving and matching the data

for (r in 1:length(rseg.model.version)) {
  split <- strsplit(params$rseg.file.path[r], split = "/")
  path_list_m2 <- as.list(split[[1]][-c(1,2,3)])
  path_string_m2 <- paste(path_list_m2, collapse = "/")
  save_url <- paste0(esite, '/', path_string_m2)
  rseg.data.r <- fread(save_url)
  assign(paste0('rseg.data.',r),rseg.data.r)
  rseg.cols.r <- names(rseg.data.r)

   if (r == 1){
      data.match <- rseg.data.r$date
      sdate <- as.Date(min(data.match))
      edate <- as.Date(max(data.match))
    } else {
      data.match <- match(data.match, rseg.data.r$date)
      sdate <- as.Date(min(data.match))
      edate <- as.Date(max(data.match))
    }
}

for (r in 1:length(rseg.model.version)) {
  rseg.flow.r <- zoo(as.numeric(as.character(rseg.data.r$Qout)), order.by = rseg.data.r$index)
  rseg.flow.r <- window(rseg.flow.r, start = sdate, end = edate)
  mode(rseg.flow.r) <- 'numeric'

  assign(paste0('rseg.flow.',r),rseg.flow.r)
}

# generate low flow data
for (r in 1:length(rseg.model.version)) {
  rseg.lowflow.r <- IHA::group2(rseg.flow.r)
  assign(paste0('rseg.lowflow.',r),rseg.lowflow.r)
}
```

## 90-Day Low Flow Comparison
```{r 90day, echo = FALSE, fig.cap=paste("The 90-day low flows:", title_param), fig.id = "90day", fig.cap.style = "Image Caption", out.width= '100%', out.height= '30%'}
for (r in 1:length(rseg.model.version)) {
  if (r == 1) {
    l90.data <- data.frame(rseg.lowflow.r$year, rseg.lowflow.r["90 Day Min"])
    colname.l90 <- paste0(dat[[r]][[3]])
  } else {
    l90.data <- cbind(l90.data, rseg.lowflow.r["90 Day Min"])
    colnames(l90.data) <- c("Year", colname.l90, paste0(dat[[r]][[3]]))
    ymax.l90 <- max(l90.data[-1])
  }
}

values.l90 <- tidyr::pivot_longer(l90.data, -Year, names_to="Model", values_to="Flow")
l90.plot <- ggplot(values.l90, aes(y=Flow, x=Year, fill = Model)) + 
    geom_bar(position="dodge", stat="identity", color="darkgrey") +
    theme_light() +
    theme(legend.title = element_text(size=10),
          legend.text = element_text(size=10),
          legend.position = "top",
          legend.key.size = unit(0.25,"cm")) +
    ylab("Flow (cfs)") +
    scale_fill_brewer()
l90.plot
```

## 30-Day Low Flow Comparison
```{r 30day, echo = FALSE, fig.cap=paste("The 30-day low flows:", title_param), fig.id = "30day", fig.cap.style = "Image Caption", out.width= '100%', out.height= '30%'}
for (r in 1:length(rseg.model.version)) {
  if (r == 1) {
    l30.data <- data.frame(rseg.lowflow.r$year, rseg.lowflow.r["30 Day Min"])
    colname.l30 <- paste0(dat[[r]][[3]])
  } else {
    l30.data <- cbind(l30.data, rseg.lowflow.r["30 Day Min"])
    colnames(l30.data) <- c("Year", colname.l30, paste0(dat[[r]][[3]]))
    ymax.l30 <- max(l30.data[-1])
  }
}

values.l30 <- tidyr::pivot_longer(l30.data, -Year, names_to="Model", values_to="Flow")
l30.plot <- ggplot(values.l30, aes(y=Flow, x=Year, fill = Model)) + 
    geom_bar(position="dodge", stat="identity", color="darkgrey") +
    theme_light() +
    theme(legend.title = element_text(size=10),
          legend.text = element_text(size=10),
          legend.position = "top",
          legend.key.size = unit(0.25,"cm")) +
    ylab("Flow (cfs)") +
    scale_fill_brewer()
l30.plot
```

## 7-Day Low Flow Comparison
```{r 7day, echo = FALSE, fig.cap=paste("The 7-day low flows:", title_param), fig.id = "7day", fig.cap.style = "Image Caption", out.width= '100%', out.height= '30%'}
for (r in 1:length(rseg.model.version)) {
  if (r == 1) {
    l7.data <- data.frame(rseg.lowflow.r$year, rseg.lowflow.r["7 Day Min"])
    colname.l7 <- paste0(dat[[r]][[3]])
  } else {
    l7.data <- cbind(l7.data, rseg.lowflow.r["7 Day Min"])
    colnames(l7.data) <- c("Year", colname.l7, paste0(dat[[r]][[3]]))
    ymax.l7 <- max(l7.data[-1])
  }
}

values.l7 <- tidyr::pivot_longer(l7.data, -Year, names_to="Model", values_to="Flow")
l7.plot <- ggplot(values.l7, aes(y=Flow, x=Year, fill = Model)) + 
    geom_bar(position="dodge", stat="identity", color="darkgrey") +
    theme_light() +
    theme(legend.title = element_text(size=10),
          legend.text = element_text(size=10),
          legend.position = "top",
          legend.key.size = unit(0.25,"cm")) +
    ylab("Flow (cfs)") +
    scale_fill_brewer()
l7.plot
```

## 1-Day Low Flow Comparison
```{r 1day, echo = FALSE, fig.cap=paste("The 1-day low flows:", title_param), fig.id = "1day", fig.cap.style = "Image Caption", out.width= '100%', out.height= '30%'}
for (r in 1:length(rseg.model.version)) {
  if (r == 1) {
    l1.data <- data.frame(rseg.lowflow.r$year, rseg.lowflow.r["1 Day Min"])
    colname.l1 <- paste0(dat[[r]][[3]])
  } else {
    l1.data <- cbind(l1.data, rseg.lowflow.r["1 Day Min"])
    colnames(l1.data) <- c("Year", colname.l1, paste0(dat[[r]][[3]]))
    ymax.l1 <- max(l1.data[-1])
  }
}

values.l1 <- tidyr::pivot_longer(l1.data, -Year, names_to="Model", values_to="Flow")
l1.plot <- ggplot(values.l1, aes(y=Flow, x=Year, fill = Model)) + 
    geom_bar(position="dodge", stat="identity", color="darkgrey") +
    theme_light() +
    theme(legend.title = element_text(size=10),
          legend.text = element_text(size=10),
          legend.position = "top",
          legend.key.size = unit(0.25,"cm")) +
    ylab("Flow (cfs)") +
    scale_fill_brewer()
l1.plot
```

## Model Performance Scatterplots

``` {r scatter.2models, echo = FALSE, fig.cap=paste("The low flow scenarios and differences between:", title_param), fig.id = "scatter1", fig.cap.style = "Image Caption", out.width = '100%',out.height = '90%'}

if (length(rseg.model.version) == 2) {

  l90.scatter <- ggplot(l90.data, aes(x = get(names(l90.data)[2]), y = get(names(l90.data)[3]))) +
  geom_point() +
  geom_smooth(formula = y ~ x, method=lm) +
  theme_light() +
  theme(axis.title.x = element_text(size = 9),
        axis.title.y = element_text(size = 9)) +
  ylab(colnames(l90.data[2])) +
  xlab(colnames(l90.data[3]))

  # L90 Error Scatterplot
  l90_diff <- unlist(l90.data[2] - l90.data[3]) # has to unlist in order to plot with ggplot!
  l90_diff_pct <- 100.0 * (l90_diff) / l90.data[3]
  
  l90.diff <- ggplot(l90.data, aes(x =get(names(l90.data)[1]), y = l90_diff)) +
    geom_point() +
    geom_smooth(formula = y ~ x, method=lm) +
    theme_light() +
    theme(axis.title.x = element_text(size = 9),
          axis.title.y = element_text(size = 9)) +
    ylab(paste("Difference: Model 1 - Model 2")) +
    xlab(paste("Year"))
  
  l30.scatter <- ggplot(l30.data, aes(x = get(names(l30.data)[2]), y = get(names(l30.data)[3]))) +
    geom_point() +
    geom_smooth(formula = y ~ x, method=lm) +
    theme_light() +
    theme(axis.title.x = element_text(size = 9),
          axis.title.y = element_text(size = 9)) +
    ylab(colnames(l30.data[2])) +
    xlab(colnames(l30.data[3]))
  
  # l30 Error Scatterplot
  l30_diff <- unlist(l30.data[2] - l30.data[3]) # has to unlist in order to plot with ggplot!
  l30_diff_pct <- 100.0 * (l30_diff) / l30.data[3]
  
  l30.diff <- ggplot(l30.data, aes(x =get(names(l30.data)[1]), y = l30_diff)) +
    geom_point() +
    geom_smooth(formula = y ~ x, method=lm) +
    theme_light() +
    theme(axis.title.x = element_text(size = 9),
          axis.title.y = element_text(size = 9)) +
    ylab(paste("Difference: Model 1 - Model 2")) +
    xlab(paste("Year"))
  
  l7.scatter <- ggplot(l7.data, aes(x = get(names(l7.data)[2]), y = get(names(l7.data)[3]))) +
    geom_point() +
    geom_smooth(formula = y ~ x,method=lm) +
    theme_light() +
    theme(axis.title.x = element_text(size = 9),
          axis.title.y = element_text(size = 9)) +
    ylab(colnames(l7.data[2])) +
    xlab(colnames(l7.data[3]))
  
  # l7 Error Scatterplot
  l7_diff <- unlist(l7.data[2] - l7.data[3]) # has to unlist in order to plot with ggplot!
  l7_diff_pct <- 100.0 * (l7_diff) / l7.data[3]
  
  l7.diff <- ggplot(l7.data, aes(x =get(names(l7.data)[1]), y = l7_diff)) +
    geom_point() +
    geom_smooth(formula = y ~ x,method=lm) +
    theme_light() +
    theme(axis.title.x = element_text(size = 9),
          axis.title.y = element_text(size = 9)) +
    ylab(paste("Difference: Model 1 - Model 2")) +
    xlab(paste("Year"))

  l1.scatter <- ggplot(l1.data, aes(x = get(names(l1.data)[2]), y = get(names(l1.data)[3]))) +
    geom_point() +
    geom_smooth(formula = y ~ x, method=lm) +
    theme_light() +
    theme(axis.title.x = element_text(size = 9),
          axis.title.y = element_text(size = 9)) +
    ylab(colnames(l1.data[2])) +
    xlab(colnames(l1.data[3]))
  
  # l1 Error Scatterplot
  l1_diff <- unlist(l1.data[2] - l1.data[3]) # has to unlist in order to plot with ggplot!
  l1_diff_pct <- 100.0 * (l1_diff) / l1.data[3]
  
  l1.diff <- ggplot(l1.data, aes(x =get(names(l1.data)[1]), y = l1_diff)) +
    geom_point() +
    geom_smooth(formula = y ~ x, method=lm) +
    theme_light() +
    theme(axis.title.x = element_text(size = 9),
          axis.title.y = element_text(size = 9)) +
    ylab(paste("Difference: Model 1 - Model 2")) +
    xlab(paste("Year"))
  
  plots <- align_plots(l90.scatter, l1.scatter, align = 'v', axis = 'l')
  plot_row1 <- plot_grid(plots[[1]], l90.diff , 
                         labels = c("90 Day Low Flow" ," "), label_size = 10,
                         rel_widths = c(0.5, 0.5))
  plot_row2 <- plot_grid(l30.scatter, l30.diff, 
                         labels = c("30 Day Low Flow" ," "), label_size = 10,
                         rel_widths = c(0.5, 0.5))
  plot_row3 <- plot_grid(l7.scatter, l7.diff, 
                         labels = c("7 Day Low Flow" ," "), label_size = 10,
                         rel_widths = c(0.5, 0.5))
  plot_row4 <- plot_grid(plots[[2]], l1.diff, 
                         labels = c("1 Day Low Flow" ," "), label_size = 10,
                         rel_widths = c(0.5, 0.5))
  
  plot_grid(plot_row1, plot_row2, plot_row3, plot_row4, ncol = 1)
} 
```

## Model %-Difference

``` {r percent, echo = FALSE, fig.cap=paste("The percent difference between the models:", title_param), fig.id = "percent", fig.cap.style = "Image Caption"}
# differences calculated in previous chunk, except the mean:

for (r in 1:length(rseg.model.version)) {
    runid.r <- runid.list[r]
    rseg.runid.r <- dat[[r]][[runid.r]]
    mean.data.r <- as.numeric(rseg.runid.r[['Qout']][['value']])
    assign(paste0('mean.data.',r), mean.data.r)
}

mean_diff <- unlist(mean.data.1 - mean.data.2) # has to unlist in order to plot with ggplot!
mean_diff_pct <- 100.0 * (mean_diff) / mean.data.2

fun_median <- function(x){
  return(data.frame(y=median(x),label=median(x,na.rm=T)))}

# setting up the comparison
perc.diff.data <- cbind(mean_diff_pct, l90_diff_pct, l30_diff_pct, l7_diff_pct, l1_diff_pct)
colnames(perc.diff.data) <- c("Mean Flow", "l90", "l30", "l7", "l1")

perc.diff.fig <- ggplot(stack(perc.diff.data), aes(x = ind, y = values)) +
  geom_boxplot(outlier.colour="red", outlier.shape=8,
                outlier.size=3) +
  stat_boxplot(geom ='errorbar') +
  theme_light() +
  ylab(paste("% Difference")) +
  xlab(paste("Flow Metric")) +
  stat_summary(fun.data = fun_median, geom="text", vjust=-0.7, 
               aes(label=round(..y.., digits = 5)))

perc.diff.fig

```

\newpage
<!---BLOCK_LANDSCAPE_START--->
# Metrics Summary

```{r StatsTable, echo=FALSE}
ft <- qflextable(statsdf)

# Set column widths
ft <- width(ft, j = 2:length(statsdf[1,]), width = 1.9)
ft <- width(ft, j = 1, width = 2.5)

# Set theme
ft <- theme_box(ft)

# Set background color of select rows --------------------------------------------------------------
ft <- bg(ft, bg = "#EFEFEF", part = "header")
ft <- bg(ft, i = ~ Description == "River Segment Model Statistics:", bg = "#EFEFEF", part = "body")
fontsize(ft, size = 9)
```
<!---BLOCK_LANDSCAPE_STOP--->

\newpage
