---
title: "Markdown Example"
output: word_document
date: "2026-07-16"
params:
  gageid: 01628500
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

See the R markdown [cheat sheet](https://rmarkdown.rstudio.com/lesson-15.HTML) for more examples. R markdown works by integrating code chunks like that below with user text and other inline code. For instance, we can see that the sqrt of 12132131 is `r round(sqrt(12132131),4)`


```{r cars}
library(dplyr)
starwars |> 
  filter(homeworld == "Tatooine",
         species == "Droid")
```

By setting *params* in the YAML (yet another markdown language) at the top of the file, we can have inputs to this markdown. For instance, the default gage id is `r params$gageid`. We can programatically control these parameters when knitting the document via:

```{r eval=FALSE}
rmarkdown::render(
  input = "PATH_TO_THIS_DOC",
  output_file = "output.docx", 
  params = list(
    gageid = "01672000"
  )
)
        
```

## Including Plots

You can also embed plots or images, for example:

```{r gageplot, echo=FALSE}
boxplot(starwars$height ~ starwars$gender)
points(x = 2,
       y = starwars$height[starwars$name == "Darth Vader"],
       pch = 15, col = "darkred")
points(x = 2,
       y = starwars$height[starwars$name == "Yoda"],
       pch = 15, col = "darkgreen")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot. More paramters are described in the cheat sheet linked above. By cliking the "knit" button in Rstudio you can see the word document output

These plots can come straight from hydrotools objects when needed:

```{r}
gage_obj <- hydrotools::WaterGageDaily$new(gage_id = params$gageid)
gage_obj$plot_percentiles()

```

And remember, now we can use that data inline. Flow two weeks ago is `r gage_obj$gage_data[gage_obj$gage_data[,gage_obj$date_col] == (Sys.Date() - 14), gage_obj$flow_col]` cfs