---
title: "August Low Flow"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dataRetrieval)
library(ggplot2)
```

## Introduction

August Low Flow values are calculated by first finding the minimum August flow for each year over a historical time period and then the median of these minimums is calculated. A boxplot illustrating the August minimum flows over the time period (2000-2019) was plotted for each of the following sites and the calculated August low flow values for each site are depicted in a table after the plots.

Site 02040000: Appomattox River

Site 02047500: Blackwater River

Site 01626000: South River

Site 01646502: Potomac River

Site 03473000: Holston River

*****        

        


The following function was used to find the minimum flow values for each August over the time period for all of the above sites.
```{r function creation}
ALF_mins <- function(site_id,start_date,end_date) {
  # first calculate min flow of each august year then find median
  #import data
  flow <- readNWISdv(site_id,'00060',start_date,end_date)
  # add the month and water year column
  date <- flow$Date
  month <- format(as.Date(date,format = '%d-%m-%Y'), '%m')
  month <- as.numeric(month)
  flow$month <- month
  flow <- addWaterYear(flow)
  #initialize mins_ap vector
  aug_mins <- c()
  w_year <- flow$waterYear[1]
  # Now evaluate
  while (w_year <= 2019) {
    w_year <- toString(w_year)
    aug <- flow[(flow$waterYear == w_year) & (flow$month == 8), ]
    min_val <- min(aug$X_00060_00003)
    aug_mins <- append(aug_mins, min_val)
    w_year <- strtoi(w_year) + 1
  }
  median_min <- median(aug_mins)
  return(aug_mins)
}
```
\pagebreak

## Site 02040000: Appomattox River

```{r appomattox}
start_date <- '1999-10-01'
end_date <- '2019-09-30'

mins_ap <- ALF_mins('02040000',start_date,end_date)
median_ap <- median(mins_ap)
ggplot(data.frame(mins_ap), aes(x = "", y = mins_ap)) + geom_boxplot() + theme_bw() +
  labs(y='Discharge [cfs]', x='August Low Flows',
       title= 'Appomattox River August Low Flows from 2000 - 2019') 

```
\pagebreak

## Site 02047500: Blackwater River
```{r blackwater river}
mins_bl <- ALF_mins('02047500',start_date,end_date)
median_bl <- median(mins_bl)
ggplot(data.frame(mins_bl), aes(x = "", y = mins_bl)) + geom_boxplot() + theme_bw() +
  labs(y='Discharge [cfs]', x='August Low Flows',
       title= 'Blackwater River August Low Flows from 2000 - 2019') 

```
\pagebreak

## Site 01626000: South River
```{r south river}
mins_so <- ALF_mins('01626000',start_date,end_date)
median_so <- median(mins_so)
ggplot(data.frame(mins_so), aes(x = "", y = mins_so)) + geom_boxplot() + theme_bw() +
  labs(y='Discharge [cfs]', x='August Low Flows',
       title= 'South River August Low Flows from 2000 - 2019')

```
\pagebreak

## Site 01646502: Potomac River
```{r potomac river}
mins_pt <- ALF_mins('01646502',start_date,end_date)
median_pt <- median(mins_pt)
ggplot(data.frame(mins_pt), aes(x = "", y = mins_pt)) + geom_boxplot() + theme_bw() +
  labs(y='Discharge [cfs]', x='August Low Flows',
       title= 'Potomac River August Low Flows from 2000 - 2019')

```
\pagebreak

## Site 03473000: Holston River
```{r holston river}
mins_hl <- ALF_mins('03473000',start_date,end_date)
median_hl <- median(mins_hl)
ggplot(data.frame(mins_hl), aes(x = "", y = mins_hl)) + geom_boxplot() + theme_bw() +
  labs(y='Discharge [cfs]', x='August Low Flows',
       title= 'Holston River August Low Flows from 2000 - 2019')

```
\pagebreak

# August Low Flow Values

 Location         | August Low Flow Value [cfs]
 -----------------|---------------------------------
 Appomattox River | `r median_ap`
 Blackwater River | `r median_bl`
 South River      | `r median_so`
 Potomac River    | `r median_pt`
 Holston River    | `r median_hl`




