---
title: "Comparison of USGS Watergage Data from Potomac River, VA & Snake River, WY"
author: "Nathaniel Abrahams"
date: "5/28/2020"
output: pdf_document
---


<style type="text/css">

h1.title {
  font-size: 39px;
  color: DarkBlue;
  text-align: center;
}
h4.author { /* Header 4 - and the author and data headers use this too  */
    font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: Black;
  text-align: center;
}
h4.date { /* Header 4 - and the author and data headers use this too  */
  font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: Black;
  text-align: center;
}
</style>

```{r include=FALSE}
library(reshape2)
library(tidyverse)
library(tidyr)
library(dplyr)
library(ggplot2)
```

## USGS Water Gages Studied

  * USGS 01646502 POTOMAC RIVER (ADJUSTED) NEAR WASH, DC 
  
  * USGS 13010065 SNAKE RIVER AB JACKSON LAKE AT FLAGG RANCH WY 
  
  *


\newpage

## Potomac River, VA (2001)


```{r, echo=FALSE}
library(dataRetrieval)

site_id <- '01646502'
startDate <- '2000-10-01'
endDate <- '2001-09-30'
pCode <-'00060'

siteinfo <- readNWISsite(site_id)
rawDailyQ <- readNWISdv(site_id, pCode, startDate, endDate)
area.sq.miles <- siteinfo$drain_area_va
normalizedDailyQ = rawDailyQ$X_00060_00003/(area.sq.miles)

plot(rawDailyQ$Date, normalizedDailyQ,
     xlab = 'Date (2001 Water Year)',
     ylab = 'Stream Discharge (cfs/sq. mile)',
     main = 'USGS 01646502 POTOMAC RIVER (ADJUSTED) NEAR WASH, DC',   
     col = 'darkblue',
     type = 'l',
     cex.axis = 0.75,
     cex.main = 1)

fig.align = 'center'

```
 


 Statistcal Value |  Discharge (cfs)                 |Discharge (cfs/sq. mile) (Normalized)
 --------------- | --------------------------------- |---------------------------
  mean           | `r mean(rawDailyQ$X_00060_00003)` |`r mean(normalizedDailyQ)`
  maximum        | `r max(rawDailyQ$X_00060_00003)`  |`r max(normalizedDailyQ)`
  minimum        | `r min(rawDailyQ$X_00060_00003)`  |`r min(normalizedDailyQ)`

                                                                                   

<br>

## Potomac River, VA (2019)


```{r, echo=FALSE}
library(dataRetrieval)

site_id <- '01646502'
startDate <- '2018-10-01'
endDate <- '2019-09-30'
pCode <-'00060'

siteinfo <- readNWISsite(site_id)
rawDailyQ <- readNWISdv(site_id, pCode, startDate, endDate)
area.sq.miles <- siteinfo$drain_area_va
normalizedDailyQ = rawDailyQ$X_00060_00003/(area.sq.miles)

plot(rawDailyQ$Date, normalizedDailyQ,
     xlab = 'Date (2019 Water Year)',
     ylab = 'Stream Discharge (cfs/sq. mile)',
     main = 'USGS 01646502 POTOMAC RIVER (ADJUSTED) NEAR WASH, DC',   
     col = 'darkblue',
     type = 'l',
     cex.axis = 0.75,
     cex.main = 1)
```
 


  Statistcal Value |  Discharge (cfs)                 |Discharge (cfs/sq. mile) (Normalized)
 --------------- | --------------------------------- |---------------------------
  mean           | `r mean(rawDailyQ$X_00060_00003)` |`r mean(normalizedDailyQ)`
  maximum        | `r max(rawDailyQ$X_00060_00003)`  |`r max(normalizedDailyQ)`
  minimum        | `r min(rawDailyQ$X_00060_00003)`  |`r min(normalizedDailyQ)`


                                                                                                   
                       
<br>

## Snake River, WY (2019)


```{r, echo=FALSE}
library(dataRetrieval)

site_id <- '13010065'
startDate <- '2018-10-01'
endDate <- '2019-09-30'
pCode <-'00060'

siteinfo <- readNWISsite(site_id)
rawDailyQ <- readNWISdv(site_id, pCode, startDate, endDate)
area.sq.miles <- siteinfo$drain_area_va
normalizedDailyQ = rawDailyQ$X_00060_00003/(area.sq.miles)

plot(rawDailyQ$Date, normalizedDailyQ,
     xlab = 'Date (2019 Water Year)',
     ylab = 'Stream Discharge (cfs/sq. mile)',
     main = 'USGS 13010065 SNAKE RIVER AB JACKSON LAKE AT FLAGG RANCH WY',   
     col = 'darkblue',
     type = 'l',
     cex.axis = 0.75,
     cex.main = 1)
```
 
   Statistcal Value |  Discharge (cfs)                 |Discharge (cfs/sq. mile) (Normalized)
 --------------- | --------------------------------- |---------------------------
  mean           | `r mean(rawDailyQ$X_00060_00003)` |`r mean(normalizedDailyQ)`
  maximum        | `r max(rawDailyQ$X_00060_00003)`  |`r max(normalizedDailyQ)`
  minimum        | `r min(rawDailyQ$X_00060_00003)`  |`r min(normalizedDailyQ)`

<br>

## Comparison Plot of Potomac River, VA (2019) & Snake River, WY (2019)

```{r, echo=FALSE}

site_id1<- '01646502'
site_id2 <- '13010065'
startDate <- '2018-10-01'
endDate <- '2019-09-30'
pCode <-'00060'

siteinfo1 <- readNWISsite(site_id1)
siteinfo2 <- readNWISsite(site_id2)

rawDailyQ1 <- readNWISdv(site_id1, pCode, startDate, endDate)
rawDailyQ2 <- readNWISdv(site_id2, pCode, startDate, endDate)

area.sq.miles1 <- siteinfo1$drain_area_va
area.sq.miles2 <- siteinfo2$drain_area_va

normalizedDailyQ1 = rawDailyQ1$X_00060_00003/(area.sq.miles1)
normalizedDailyQ2 = rawDailyQ2$X_00060_00003/(area.sq.miles2)

plot(rawDailyQ$Date,normalizedDailyQ1, 
     xlab = 'Date (2019 Water Year)',
     ylab = 'Stream Discharge (cfs/sq. mile)',
     main = 'Potomac River, VA & Snake River, WY Discharge (Normalized over Drainage Area)',
     col = 'darkblue',
     type = 'l',
     cex.axis = 0.7,
     cex.main = 0.9,)

lines(rawDailyQ$Date,normalizedDailyQ2,type = 'l', col = 'red')

legend('topright', 
       legend = c('USGS 01646502 - Potomac River, VA','USGS 13010065 - Snake River, WY'), 
       col= c('darkblue', 'red'),
       lty = 1:1,
       lwd = 2,
       cex = 0.53)

```

## Comparison Plot of Potomac River, VA (2019) & Snake River, WY (2019) (ggplot2)


```{r,echo=FALSE}
library(tidyverse)
site_id <- '01646502'
startDate <- '2018-10-01'
endDate <- '2019-09-30'
pCode <-'00060'
siteinfo <- readNWISsite(site_id)
rawDailyQ <- readNWISdv(site_id, pCode, startDate, endDate)

date<- rawDailyQ$Date
PotomacRiverVA <-normalizedDailyQ1
SnakeRiverWY <-normalizedDailyQ2
nq <- data.frame(PotomacRiverVA,SnakeRiverWY)
Q <- data.frame(date, nq)

library(ggplot2)
ggplot(Q, 
       aes(x=date, y=PotomacRiverVA)) +
       geom_line(color='darkblue')+
       labs(title='USGS 01646502 POTOMAC RIVER (ADJUSTED) NEAR WASH, DC',
       x='Date (2019 Water Year)', 
       y='Discharge (cfs/sq. mile)' )+
       theme(
        plot.title = element_text(size = 12, face = "bold",  hjust = 0.5))+
     scale_y_log10()

```

```{r,echo=FALSE}

library(tidyverse)
site_id <- '13010065'
startDate <- '2018-10-01'
endDate <- '2019-09-30'
pCode <-'00060'
siteinfo <- readNWISsite(site_id)
rawDailyQ <- readNWISdv(site_id, pCode, startDate, endDate)

date<- rawDailyQ$Date
PotomacRiverVA <-normalizedDailyQ1
SnakeRiverWY <-normalizedDailyQ2
nq <- data.frame(PotomacRiverVA,SnakeRiverWY)
Q <- data.frame(date, nq)

library(ggplot2)
ggplot(Q, 
       aes(x=date, y=SnakeRiverWY)) +
       geom_line(color='darkblue')+
       labs(title='USGS 13010065 SNAKE RIVER AB JACKSON LAKE AT FLAGG RANCH WY',
       x='Date (2019 Water Year)',
       y='Discharge (cfs/sq. mile)' )+
       theme(
        plot.title = element_text(size = 12, face = "bold",  hjust = 0.5))+
     scale_y_log10()

```

```{r,echo=FALSE}

library("reshape2")
library(tidyverse)

site_id <- '01646502'
startDate <- '2018-10-01'
endDate <- '2019-09-30'
pCode <-'00060'

siteinfo <- readNWISsite(site_id)
rawDailyQ <- readNWISdv(site_id, pCode, startDate, endDate)

Q <- melt(Q, id.vars="date")


 ggplot(data=Q, aes(x= date , y = value, group = variable, colour =    
        variable)) +
        labs(title = "Comparison of Potomac River, VA & Snake River, WY Discharge 
        (Normalized over Area)", x = "Date (2019 Water Year)", 
        y = "Discharge (depth/year)",          
        color = "River Segment\n") +
        scale_color_manual(labels = c("USGS 01646502 - Potomac", "USGS 13010065 - Snake"),            
                           values = c("darkblue", "red"))+
        geom_line() + theme(
        plot.title = element_text(size = 10, face = "bold",  hjust = 0.5))      

```




```{r,echo=FALSE}

#boxplot Potomac outliers out (regular years, no if else structure)
library(tidyverse)

site_id <- '01646502'
startDate <- '2000-01-01'
endDate <- '2019-12-31'
pCode <-'00060'

siteinfo <- readNWISsite(site_id)
rawDailyQ <- readNWISdv(site_id, pCode, startDate, endDate)
Date = rawDailyQ$Date
Year = format(as.Date(Date, format = "%d/%m/%Y"),"%Y")
rawDailyQ <- data.frame(rawDailyQ, Year)

ggplot(rawDailyQ, 
  aes(x=Year, y = X_00060_00003))+
  geom_boxplot(outlier.shape = NA)+
  labs(title= 'USGS 01646502 POTOMAC RIVER (ADJUSTED) NEAR WASH, DC')+
  ylab('Discharge (cfs)')+ 
  xlab('Year')+
  geom_point(color='red', 
             stat = 'summary',
             fun = 'mean')+
  theme_bw()+
  theme(plot.title = element_text(size = 12, face = "bold",  hjust = 0.5))+
  coord_cartesian(ylim=c(0, 75000))
```
  
           
```{r, echo=FALSE}

library(tidyverse)

site_id <- '01646502'
startDate <- '2000-10-01'
endDate <- '2019-09-30'
pCode <-'00060'

siteinfo <- readNWISsite(site_id)
rawDailyQ <- readNWISdv(site_id, pCode, startDate, endDate)
Date <- rawDailyQ$Date

Year<-format(as.Date(Date, format = "%d/%m/%Y"),"%Y")

Month<-format(as.Date(Date, format = "%d/%m/%Y"),"%m")
Day<-format(as.Date(Date, format = "%d/%m/%Y"),"%d")

Month <- as.numeric(Month)
Day <- as.numeric(Day)
Year<- as.numeric(Year)

WaterYear<-Year


for (i in 1:6939) {
  if (Month[i] >= 10 ){
    WaterYear[i]<- WaterYear[i]+1
    }
}

ggplot(rawDailyQ, 
  aes(x=factor(WaterYear), y = X_00060_00003))+
  geom_boxplot(outlier.shape = NA)+
  geom_point(color='red', 
             stat = 'summary',
             fun = 'mean')+
  labs(title= 'USGS 01646502 POTOMAC RIVER (ADJUSTED) NEAR WASH, DC')+
  ylab('Discharge (cfs)')+ 
  xlab('Water Year')+
  theme_bw()+
  theme(plot.title = element_text(size = 12, face = "bold",  hjust = 0.5))+
  coord_cartesian(ylim=c(0, 70000))

```


```{r, echo=FALSE}

library(tidyverse)

site_id <- '13010065'
startDate <- '2000-10-01'
endDate <- '2019-09-30'
pCode <-'00060'

siteinfo <- readNWISsite(site_id)
rawDailyQ <- readNWISdv(site_id, pCode, startDate, endDate)
Date <- rawDailyQ$Date

Year<-format(as.Date(Date, format = "%d/%m/%Y"),"%Y")

Month<-format(as.Date(Date, format = "%d/%m/%Y"),"%m")
Day<-format(as.Date(Date, format = "%d/%m/%Y"),"%d")

Month <- as.numeric(Month)
Day <- as.numeric(Day)
Year<- as.numeric(Year)

WaterYear<-Year


for (i in 1:6939) {
  if (Month[i] >= 10 ){
    WaterYear[i]<- WaterYear[i]+1
    }
}

ggplot(rawDailyQ, 
  aes(x=factor(WaterYear), y = X_00060_00003))+
  geom_boxplot(outlier.shape = NA)+
  labs(title= 'USGS 13010065 SNAKE RIVER AB JACKSON LAKE AT FLAGG RANCH WY')+
  ylab('Discharge (cfs)')+ 
  xlab('Water Year')+
  geom_point(color='red', 
             stat = 'summary',
             fun = 'mean')+
  theme_bw()+
  theme(plot.title = element_text(size = 12, face = "bold",  hjust = 0.5))+
  coord_cartesian(ylim=c(0, 2100))
```

```{r,echo=FALSE}

library(tidyverse)

site_id <- '01646502'
startDate <- '2009-10-01'
endDate <- '2019-09-30'
pCode <-'00060'

siteinfo <- readNWISsite(site_id)
rawDailyQ <- readNWISdv(site_id, pCode, startDate, endDate)
Date <- rawDailyQ$Date

Year<-format(as.Date(Date, format = "%d/%m/%Y"),"%Y")
Month<-format(as.Date(Date, format = "%d/%m/%Y"),"%m")
Day<-format(as.Date(Date, format = "%d/%m/%Y"),"%d")

Month <- as.numeric(Month)
Day <- as.numeric(Day)
Year<- as.numeric(Year)

WaterYear<-Year


for (i in 1:length(Month)) {
  if (Month[i] >= 10 ){
    WaterYear[i]<- WaterYear[i]+1
  }
}

rawDailyQ <- data.frame(rawDailyQ, WaterYear, Month)
rawDailyQsummer <- filter(rawDailyQ, Month %in% c(6:8))

ggplot(rawDailyQsummer, 
  aes(x=factor(WaterYear), y = X_00060_00003))+
  geom_boxplot(outlier.shape = NA)+
  labs(title= 'USGS 01646502 POTOMAC RIVER (ADJUSTED) NEAR WASH, DC')+
  ylab('Discharge (cfs)')+ 
  xlab('Summer Months (June-August)')+
  geom_point(color='red', 
             stat = 'summary',
             fun = 'mean')+
  theme_bw()+
  theme(plot.title = element_text(size = 12, face = "bold",  hjust = 0.5))+
  coord_cartesian(ylim=c(0, 55000))
```



```{r,echo=FALSE}


library(tidyverse)
site_id <- '01646502'
startDate <- '2009-10-01'
endDate <- '2019-09-30'
pCode <-'00060'

siteinfo <- readNWISsite(site_id)
rawDailyQ <- readNWISdv(site_id, pCode, startDate, endDate)
Date <- rawDailyQ$Date

#rawDailyQ <- addWaterYear(rawDailyQ)

Year<-format(as.Date(Date, format = "%d/%m/%Y"),"%Y")
Month<-format(as.Date(Date, format = "%d/%m/%Y"),"%m")
Day<-format(as.Date(Date, format = "%d/%m/%Y"),"%d")

Month <- as.numeric(Month)
Day <- as.numeric(Day)
Year<- as.numeric(Year)

WaterYear<-Year


for (i in 1:length(Month)) {
  if (Month[i] >= 10 ){
    WaterYear[i]<- WaterYear[i]+1
  }
}

rawDailyQ <- data.frame(rawDailyQ, WaterYear, Month)
rawDailyQwinter <- filter(rawDailyQ, Month %in% c(12,1,2))

ggplot(rawDailyQwinter, 
  aes(x=factor(WaterYear), y = X_00060_00003))+
  geom_boxplot(outlier.shape = NA)+
  labs(title= 'USGS 01646502 POTOMAC RIVER (ADJUSTED) NEAR WASH, DC')+
  ylab('Discharge (cfs)')+ 
  xlab('Winter Months (December-February)')+
  geom_point(color='red', 
             stat = 'summary',
             fun = 'mean')+
  theme_bw()+
  theme(plot.title = element_text(size = 12, face = "bold",  hjust = 0.5))+
  coord_cartesian(ylim=c(0, 75000))
```


```{r, echo=FALSE,results='hide',fig.keep='all'}


library(dataRetrieval)
library(tidyverse)

#startDate <- '2017-4-14'
#endDate <- '2019-09-30'

parameterCd	 <- '00060'
siteNumbers <- '13010065'

stat <- readNWISstat(
  siteNumbers,
  parameterCd,
  startDate = "",
  endDate = "",
  convertType = TRUE,
  statReportType = "daily",
  statType = "mean"
)


ggplot(stat, 
  aes(x=factor(month_nu), y = mean_va))+
  geom_boxplot(outlier.shape = NA)+
  labs(title= 'USGS 13010065 SNAKE RIVER, Mean Daily Discharge (1984-2019), Grouped by Month ')+
  ylab('Mean Daily Discharge (cfs)')+ 
  xlab('Month')+
  geom_point(color='red', 
             stat = 'summary',
             fun = 'mean')+
  theme_bw()+
  theme(plot.title = element_text(size = 10, face = "bold",  hjust = 0.5))+
  coord_cartesian(ylim=c(0, 4600))

```


```{r, echo=FALSE}

#San Diego GroundWater

library(dataRetrieval)
library(tidyverse)

# startDate <- '2009-10-01'
# endDate <- '2019-09-30'

pCode <-'00060'
siteNumbers <- '323808117060402'


gw<-readNWISgwl(
  siteNumbers,
  startDate = "",
  endDate = "",
  convertType = TRUE,
  tz = "UTC")

ggplot(gw, 
  aes(x=lev_dt, y=lev_va))+
  geom_point()+
  geom_line()+
  geom_smooth(method = 'lm', formula= y~x)+
  labs(title='USGS 323808117060402 018S002W05J002S, San Diego County, CA', x= 'Date', y= "Groundwater Level Below Land Surface (ft)")+
  scale_y_continuous(trans = "reverse")+

  theme_bw()+
  theme(plot.title = element_text(size = 12, face = "bold",  hjust = 0.5))
```

```{r, echo=FALSE}

#San Diego GroundWater

library(dataRetrieval)
library(tidyverse)

startDate <- '2017-4-14'
# endDate <- '2019-09-30'
pCode <-'00060'
siteNumbers <- '393749079190301'


gw<-readNWISgwl(
  siteNumbers,
  startDate = "",
  endDate = "",
  convertType = TRUE,
  tz = "UTC")

date <- gw$lev_dt
gw <- mutate(gw, year = format(as.Date(date, format = "%d/%m/%Y"),"%Y"))
gw <- filter(gw, year >= 2017)


ggplot(gw, 
  aes(x=lev_dt, y=lev_va))+
  geom_point()+
  geom_line()+
  geom_smooth(method = 'lm', formula= y~x)+
  labs(title='UUSGS 393749079190301, Garret County, MD', x= 'Date', y= "Groundwater Level Below Land Surface (ft)")+
  scale_y_continuous(trans = "reverse")+

  theme_bw()+
  theme(plot.title = element_text(size = 12, face = "bold",  hjust = 0.5))
```




