---
title: "An Analysis of USGS Gauge Mean Streamflow for Winter and Spring from 2000 to Present"
author: "Ella Fox, Glenn Campagna and Megan Pritchard"
date: "5/15/2023"
output:
  html_document:
    df_print: paged
  word_document: default
  pdf_document: default
geometry: left=2cm, right=3cm
params:
  doc_title: "USGS Gauge Mean Stremflow Winter/Spring"
  rseg.gauge: ["01636500","01668000","02037500","03529500", "03532000", "03524000", "03527220","02066000" ] #overidden by params in render cmnd
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Starting Info 

Scope: Develop RMD workflow to characterize USGS gauge mean streamflow for Winter (Dec-March) and Spring (April-present) from 2000 to present. Create visualization to highlight winters/springs that are above/below long-term winter mean and spring mean.

Context: Previous research has shown that the amount of winter recharge, that is precipitation that infiltrates into groundwater, is an indicator of the subsequent summer streamflow. Thus, low winter recharge (indicated by streamflow between Dec-March) is a warning indicator for potential summer drought conditions. While Joey/DEQ have tools at the ready for drought prediction, the casual hydrologist may wonder things like seems like the hiking trails are dry this time year, is this just me or backed up with data? or I had to mow my grass before April the year...I wonder if the early leaf-on will result in sustained evapotranspiration that reduces water storage to the point of impacting summer streamflow?

## List of gauge numbers used and why 
Locations downstream are better within larger rivers to represent large basins. Locations in drought conditions are also of interest. The locations need to be above the fall line which is between the Coastal Plain and Piedmont regions of VA, because flow downstream of the fall line is tidally influenced

Some rivers/basins in VA currently impacted by dry conditions:  

01636500: Shenandoah (into Potomac) 
01668000: Rappahannock (Fredericksburg)  
02037500: James (Richmond)    
03529500: Powell (Big stone gap VA)  
03532000: Powell (Arthur TN)  
03524000: Clinch (Cleveland VA)  
03527220: Clinch (Looneys gap TN)   
02066000: Roanoke (Randolph VA)  



## Retrieving data from the USGS
```{r, include=FALSE}
#calling packages needed

library(zoo)
#library(IHA)  #Package not available for this version of R
#install.packages("dataRetrieval")
library(dataRetrieval)
library(dplyr)
  #megan had dependency issues loading "dplyr" and had to do this:
  #library(devtools)
  #remove.packages("cli")
  #install.packages("cli")
  #install_version("vctrs", version = "0.5.0", repos = "http://cran.us.r-project.org")
library(ggplot2)
  #to load ggplot2, had to update dependency "rlang" by doing this:
  #remove.packages("rlang")
  #install.packages("rlang")
library(knitr)
library(tidyverse)
library(pals)
library(lubridate)
library(stats)
library(ggbreak)
```

```{r}
#Retrieve daily flow data for desired river basin gauge
startDate <- '2000-01-01'#from 2000 to present date
endDate <- '2023-12-31'
pCode <- '00060' #the code for discharge in cfs
sCode <- '00003' #the code for daily mean data

RRflow <- readNWISdv(params$rseg.gauge, pCode, startDate, endDate, sCode) #rseg.gauge should be given in render cmnd
colnames(RRflow) <- c('Agency', 'Site No', 'Date', 'Flow', 'Code') #rename the columns for table
head(RRflow, 3) #preview flow data
```
# Data Analysis

## Subset Data 
```{r, echo=FALSE, message=FALSE, warning=FALSE}
#subset data into years and then into seasons/months for analysis
#Winter(Dec-March) & Spring(April-Present)
  
RRflow$Date <- as.Date(RRflow$Date, format= "%m/%d/%Y")
RRflow$month <-month(RRflow$Date)
RRflow$year <- year(RRflow$Date)

#Create spring monthly average
Springmon= c(4,5,6)
RRspring <- RRflow %>%
  mutate(month=RRflow$month, year=RRflow$year) %>%
  group_by(year, month) %>%
  summarize(SmonthMean= mean(Flow)) %>% #same as summarize(group_by(RRflow, year, month), mean(Flow))
  filter(month == Springmon)
head(RRspring,3)

#create winter monthly average
Wintermon= c(1,2,3,12)
RRwinter <- RRflow %>%
  mutate(month=RRflow$month, year=RRflow$year) %>%
  group_by(year, month) %>%
  summarize(WmonthMean= mean(Flow)) %>%
  filter(month==Wintermon)
head(RRwinter,3)
```

## Long-term average Spring & Winter Flows:

```{r, echo=FALSE}
#Long-term averages for winter and spring seasons
winterAvg <- mean(RRwinter$WmonthMean)
springAvg <- mean(RRspring$SmonthMean)

paste0('Winter Average Flow: ',round(winterAvg, digits = 2), ' cfs')
paste0('Spring Average Flow: ',round(springAvg, digits = 2), ' cfs')
```

## How does this year compare to those long-term averages?

```{r, echo=FALSE}
#Comparing this year's flow with those averages
spring23 <- RRspring %>% filter(year==2023) # finding avg for this years flow
winter23 <- RRwinter %>% filter(year==2023)
spring23avg <- mean(spring23$SmonthMean)
winter23avg <- mean(winter23$WmonthMean)
#Finding percentage difference 
springPct <- ((spring23avg - springAvg)/springAvg)*100
winterPct <- ((winter23avg - winterAvg)/winterAvg)*100
paste0('Winter Flow Difference: ',round(springPct, digits = 1), '%')
paste0('Spring Flow Difference: ',round(winterPct, digits = 1), '%')

#Getting monthly average flows for the time period
monthlyFlow = aggregate(RRflow$Flow, list(RRflow$month, RRflow$year), FUN = 'mean')
colnames(monthlyFlow) <- c('month','year','flow')

#Getting winters and springs:
springFlows <- monthlyFlow %>% filter(month==4|month==5|month==6)
winterFlows <- monthlyFlow %>% filter(month==12|month==1|month==2|month==3)
```



```{r, include=FALSE}
## What months were the biggest differences?
#Finding monthly long-term averages:
dec <- RRwinter %>% filter(month == 12)
decAvg <- mean(dec$WmonthMean)
jan <- RRwinter %>% filter(month == 1)
janAvg <- mean(jan$WmonthMean)
feb <- RRwinter %>% filter(month == 2)
febAvg <- mean(feb$WmonthMean)
mar <- RRwinter %>% filter(month == 3)
marAvg <- mean(mar$WmonthMean)
apr <- RRspring %>% filter(month == 4)
aprAvg <- mean(apr$SmonthMean)
may <- RRspring %>% filter(month == 5)
mayAvg <- mean(may$SmonthMean)
jun <- RRspring %>% filter(month == 6)
junAvg <- mean(jun$SmonthMean)
#Finding 2022-2023 monthly averages ...
 # in progress
```



##Visualization 

```{r, echo=FALSE}
#Seasonal averages per year
winterYrAvg <- aggregate(winterFlows$flow, by = list(RRwinter$year), FUN = 'mean')
colnames(winterYrAvg) <- c('year','flow')
springYrAvg <- aggregate(springFlows$flow, by = list(springFlows$year), FUN = 'mean')
colnames(springYrAvg) <- c('year','flow')

ggplot(winterYrAvg, aes(x=year, y=flow)) + geom_point(aes(col = 'blue')) + geom_point(data = springYrAvg, aes(x=year, y=flow, col = 'red')) +
  scale_color_identity(name = NULL, breaks=c('red','blue'), labels = c('Spring','Winter'), guide = 'legend') + 
  scale_x_continuous(breaks = seq(min(winterYrAvg$year), max(winterYrAvg$year), by = 2)) + 
  labs(x='Year', y= 'Seasonal Avg Flow (cfs)') +
  ggtitle("Winter and Spring Avg Flows (2000 - Present)")
```


## Spring Averages Per Month Graphs

```{r, echo=FALSE}
#highlight winters/springs that are above/below long-term winter mean and spring mean
#how spring and winter average flows change over 2000 to now 

#Plot of all years with month avg vs time for spring
ggplot(RRspring, aes(x=month, y=SmonthMean, color=as.factor(year))) + geom_point(size=2) + xlab("Spring Months")+ ylab("Spring Month Flow Mean(cfs)")+theme_minimal()+scale_x_continuous(breaks=seq(4,6,by=1)) + guides(color= guide_legend(title = "Years"))+geom_line()+ggtitle("Mean Flow for Spring(2000-Present)")

  
```

```{r, echo=FALSE}
#Plot of current year, drought year and average year for spring 

RRspringN <- RRspring %>% filter(year %in% c("2002", "2023")) #Adjust original RRspring to only include 2002 and 2023, current and drought year

RRspringAVG <- RRflow %>% #adjust RRflow original to collect the monthly average in spring for all years
  mutate(month=RRflow$month, year=RRflow$year) %>%
  group_by(month) %>%
  summarize(SmonthMean= mean(Flow)) %>%
  filter(month == Springmon)
#RRspringAVG

comRR <- rbind(RRspringN, RRspringAVG) #combine the two datasets to make easier graphing 

#create graph
ggplot(comRR, aes(x=month, y=SmonthMean, color=as.factor(year))) + geom_point(size=2) + xlab("Spring Months")+ ylab("Spring Month Flow Mean(cfs)")+theme_minimal()+scale_x_continuous(breaks=seq(4,6,by=1)) + guides(color= guide_legend(title = "Years")) +geom_line()+scale_color_manual(labels=c("2002","2023","Average"), values=c('#00AFBB','#FC4E07','#E7B800'))+ggtitle("Average Flow for Spring for Drought Year & Present Year Vs. All Years Mean")
```

## Winter Averages Per Month Graphs

```{r, echo=FALSE}
#Plot of all years with month avg vs time for winter

ggplot(RRwinter, aes(x=month, y=WmonthMean, color=as.factor(year))) + geom_point(size=2) + xlab("Winter Months")+ ylab("Winter Month Flow Mean(cfs)")+theme_minimal() + guides(color= guide_legend(title = "Years")) +ggtitle("Mean Flow for Winter(2000-Present)")+scale_x_continuous(breaks=seq(1,12,by=1)) +scale_x_break(c(3,12),scales=0.5)+geom_line()

```

```{r, echo=FALSE}
#Plot of current year, drought year and average year for winter

RRwinterN <- RRwinter %>% filter(year %in% c("2002", "2023")) #Adjust original RRwinter to only include 2002 and 2023, current and drought year

RRwinterAVG <- RRflow %>% #adjust RRflow original to collect the monthly average in winter for all years
  mutate(month=RRflow$month, year=RRflow$year) %>%
  group_by(month) %>%
  summarize(WmonthMean= mean(Flow)) %>%
  filter(month == Wintermon)
#RRwinterAVG

comRR <- rbind(RRwinterN, RRwinterAVG) #combine the two datasets to make easier graphing 

#create graph
ggplot(comRR, aes(x=month, y=WmonthMean, color=as.factor(year))) + geom_point(size=2) + xlab("Winter Months")+ ylab("Winter Month Flow Mean(cfs)")+theme_minimal()+scale_x_continuous(breaks=seq(1,12,by=1)) + guides(color= guide_legend(title = "Years")) +geom_line()+scale_color_manual(labels=c("2002","2023","Average"), values=c('#00AFBB','#FC4E07','#E7B800'))+ggtitle("Average Flow for Winter for Drought Year & Present Year Vs. All Years Mean")+scale_x_break(c(3,12),scales=0.5)
```
## Boxplots
```{r, echo=FALSE}
par(mfrow=c(1,2)) #creates 2 windows side-by-side for the plots to be shown
boxplot(RRwinter$WmonthMean, ylab = 'Monthly magnitude (cfs)', main = 'Monthly Mean Winter', ylim= c(0,10000), col='#FC4E07')
boxplot(RRspring$SmonthMean, ylab = 'Monthly magnitude (cfs)', main = 'Monthly Mean Spring', ylim= c(0,10000), col='#00AFBB')
```


```{r, Boxplots of Mean Flow by Year & Season, echo=FALSE}
#create dataframe
colnames(RRspring) <- c('year', 'month', 'mean')
colnames(RRwinter) <- c('year', 'month', 'mean')
yr_avgs <- rbind(RRwinter, RRspring)
yr_avgs <- arrange(yr_avgs, year)

for(i in Springmon){
  yr_avgs$month <- gsub(i,'spring',yr_avgs$month)
}

for(i in c(12,1,2,3)){ #12 has to be first or '12' becomes 'winterwinter' from the 1 and 2
  yr_avgs$month <- gsub(i,'winter',yr_avgs$month)
}

#Note about plots: must say x=factor(year) to make it a discrete variable so that the fill by month works

#paired boxplot:
ggplot(yr_avgs, aes(x=factor(year),y=mean, fill=month)) + 
  geom_boxplot() + 
  xlab("Year") + ylab("Flow (cfs)") + ggtitle("Seasonal Mean Flow By Year") +
  scale_y_continuous(minor_breaks=seq(0,max(yr_avgs$mean),500)) +
  guides(fill=guide_legend(title="Season:")) +
  theme(axis.text.x=element_text(size=9,angle=90),
        axis.text.y=element_text(size=7),
        legend.text=element_text(size=8),
        legend.title=element_text(face="bold",size=8),
        legend.position="top",
        legend.key.height=unit(0.5,'cm'),
        legend.margin=margin(0,0,0,0),
        panel.grid.major.x=element_line(colour="light gray"))
```


```{r, echo=FALSE}
#faceted by season:
ggplot(yr_avgs, aes(x=factor(year),y=mean, fill=month)) + 
  geom_boxplot() + 
  facet_wrap(~month, scales="fixed") +
  xlab("Year") + ylab("Flow (cfs)") + ggtitle("Seasonal Mean Flow By Year") +
  scale_y_continuous(minor_breaks=seq(0,max(yr_avgs$mean),500)) +
  guides(fill=guide_legend(title="Season:")) +
  theme(axis.text.x=element_text(size=7,angle=90),
        axis.text.y=element_text(size=7),
        strip.text=element_text(face="bold",size=8,
                                        margin=margin(3,0,3,0)),
        legend.position="none",
        panel.grid.major.x=element_line(colour="light gray"))
```


```{r, echo=FALSE}
#faceted by year:
ggplot(yr_avgs, aes(x=factor(year),y=mean, fill=month)) + 
  geom_boxplot() + 
  facet_wrap(~year, ncol=6, scales="free", strip.position="right") +
  xlab("Year") + ylab("Flow (cfs)") + ggtitle("Seasonal Mean Flow By Year") +
  guides(fill=guide_legend(title="Season:")) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.text.y=element_text(size=6),
        strip.text.y.right=element_text(face="bold",size=8,
                                        margin=margin(0,1,0,2)),
        legend.text=element_text(size=7),
        legend.title=element_text(face="bold",size=7),
        legend.key.size=unit(0.5, 'cm'),
        legend.position="top",
        legend.key.height=unit(0.4,'cm'),
        legend.margin=margin(0,0,0,0),
        panel.spacing=unit(0.1,'cm'))

```



