---
header-includes: \pagenumbering{gobble}
output:
  pdf_document: default
    
---
```{r inputs, include=FALSE, echo=FALSE}
# INPUTS ------------------------------------------------------------------
# Link to hydro-tools folder within GitHub folder
basepath='C:\\Users\\danie\\Documents\\HARP\\GitHub\\hydro-tools';

# Address of "DEQ_Model_vs_USGS_Comparison" folder
# Include "DEQ_Model_vs_USGS_Comparison" in address!
container <- paste0(basepath, "\\HARP-2018\\DEQ_Model_vs_USGS_Comparison_Northern")

# USGS Gage number
siteNo <- "01653000"
# CARRYOVER IF MASTER IS BEING RUN ----------------------------------------
if (exists("container.master") == TRUE) {
  container <- container.master
  siteNo <- siteNo.master
  new.or.original <- new.or.original.master
}

# LINKING MODEL SEGMENT ---------------------------------------------------

gage.to.segment <- read.csv(file.path(container, "data", "Gage_To_Segment_Northern.csv"),
                            header = TRUE, sep = ',', stringsAsFactors = FALSE)
gage.to.segment <- subset(gage.to.segment, gage.to.segment$gage == as.numeric(siteNo))
RivSeg <- gage.to.segment$segment
```
---
title: |
    | Appendix B.23: USGS Gage `r paste(siteNo, "vs.", RivSeg)`
    | Lower Potomac River
output:
  pdf_document: default
---
```{r, include=FALSE, echo=FALSE}
# Should new or original data be used?
new.or.original <- "new"

site <- "http://deq2.bse.vt.edu/d.dh"    #Specify the site of interest, either d.bet OR d.dh



source(paste(basepath,'config.local.private',sep='/'));
source(paste(hydro_tools,"VAHydro-2.0/rest_functions.R", sep = "/")); 
#source(paste(hydro_tools, "HARP-2018/DEQ_Model_vs_USGS_Comparison_Northern/code/fn_gage+seg_mapper.R", sep = "/"));
source(paste(hydro_tools, "HARP-2018/DEQ_Model_vs_USGS_Comparison_Northern/code/fn_gage+seg_mapper_fromNWIS.R", sep = "/"));
#retrieve rest token
source(paste(hydro_tools,"auth.private", sep = "/"));#load rest username and password, contained in auth.private file
token <- rest_token(site, token, rest_uname, rest_pw);
options(timeout=120); # set timeout to twice default level to avoid abort due to high traffic

```
```{r error, include=FALSE}
# DOCUMENTATION -----------------------------------------------------------

# Creates plots zoomed in three-month periods of highest error, also calculates
# a few metrics pertaining to error -- such as percent of observations above 20%

library(zoo)
library(lubridate)
library(knitr)
library(ggplot2)
library(readr)
library(magick)

# INPUTS ----------------------------------------------------



# NEW OR ORIGINAL DATA SWITCH ---------------------------------------------

if (new.or.original == "new") {
  container.cont <- "\\data\\new_(updated)_data"
} else if (new.or.original == "original") {
  container.cont <- "\\data\\original_(reproducible)_data"
} else {
  print("ERROR: neither new or original data specified")
}

# LOADING DATA ------------------------------------------------------------

description <- read_file(paste0(container, "\\gage_descriptions\\", siteNo, ".txt"))

# TEXT ------
data <- read.csv(paste0(container, container.cont, "\\derived_data\\trimmed+area-adjusted_data\\",siteNo,"_vs_",RivSeg, " - Derived Data.csv"))

# GIS ------
# Generating gage location maps
gis_img <- fn_gage_and_seg_mapper(RivSeg, siteNo, site, hydro_tools, token)


# OVERALL MEAN FLOW
met00_Gage_MeanFlow <- signif(mean(data$gage.flow), digits=3);
met00_Model_MeanFlow <- signif(mean(data$model.flow), digits=3);
met00_PctError <- -(signif(((met00_Model_MeanFlow - met00_Gage_MeanFlow) / met00_Gage_MeanFlow)*100, digits=3));

# Calculating mean flow of gage and model
avg_gage <- mean(data$gage.flow)
avg_model <- mean(data$model.flow)

# ADDING ADDITIONAL DATA COLUMNS ------------------------------------------
data$year <- year(ymd(data$date))
data$month <- month(ymd(data$date))
data$day <- day(ymd(data$date))

data$date <- as.Date(data$date)
start.date <- data$date[1]
end.date <- data$date[length(data$date)]
DumYear <- data.frame(as.Date(seq(as.Date(start.date), as.Date(end.date), by = 'day')))
colnames(DumYear) <- 'date'
data <- merge.data.frame(data, DumYear, by="date", all=TRUE)



# initialize variables ----------------------------------------------------
# This section will create a hydrograph that will zoom in on 3 month segments where error is high
# It does so for the top three highest error periods

#all_data puts model gage flows and corresponding dates in one data frame
all_data <- data.frame(data$date, data$model.flow, data$gage.flow) 
all_data$counter <- 1:length(all_data$data.date) # counter fixes issues with row numbers later on in script
colnames(all_data) <- c('Date', 'Model Flow', 'Gage Flow', 'Counter')

# find the first date for which data is collected, (in date format)
# and a date that is roughly one year and two months past the first date
YearStart <- as.character(as.Date(all_data$Date[1]))     
fixer <- which(all_data$Date == paste0(year(YearStart)+1,"-11-30"))
YearEnd <- as.character(as.Date(all_data$Date[fixer]))

# YearStart_Row and YearEnd_Row are the rows corresponding the the YearStart and YearEnd dates
YearStart_Row <- as.numeric(which(all_data$Date==YearStart)) 
YearEnd_Row <- as.numeric(which(all_data$Date==YearEnd))

# initalize dataframes and counters, assign names for dataframe columns
#AvgMonthlyError: used within nested for loop to create a 1x12 matrix that holds 1 year of 3 month error segments
#Timespan_Error: used in large loop to store values from AvgMonthlyError; holds entire timespan of 3 month error segments
AvgMonthlyError <- data.frame(matrix(nrow=1,ncol=1));  
names(AvgMonthlyError)<-'Error' 
Timespan_Error <- data.frame(matrix(nrow=1, ncol=1)); 
names(Timespan_Error)<-'Error'
i <- 1; # used for first for loop to advance a year
x <- 1 # x and y used to advance dataframes
y <- 12

# start loops used for yearly and monthly data  -------------------------------------------------------------

loop <- as.numeric(round(length(data$date)/365, digits = 0))-1
for (i in 1:loop){                                # run loop for an entire data series
  year <- all_data[YearStart_Row:YearEnd_Row,] # specify year: 10-01-year1 to 11-30-year2
  m <- 1                                        # counter for nested loop
  
  MonthStart <- YearStart  # first date for 3 month timespan                      
  doi <- as.Date(MonthStart) 
  doi <- doi + seq(0,365,31) 
  # doi= date of interest. dummy variable just to create the function next.month
  next.month <- function(doi) as.Date(as.yearmon(doi) + 1/12) + as.numeric(as.Date(doi)-(as.Date(as.yearmon(doi))))
  
  #(re)initalize variables for the nested loop
  MonthEnd <-data.frame(next.month(doi));  # last date in 3 month timespan - used function to determine 3rd month
  MonthEnd <- MonthEnd[3,1]-2 # specifies end of month 3 as last date
  # (technically specifies 01 of month 4)
  
  # row numbers corresponding with start and end dates, as a number. See note below 
  MonthStart_Row <- as.numeric(which(as.Date(all_data$Date)==as.Date(MonthStart)))
  MonthEnd_Row <- as.numeric(which(as.Date(all_data$Date)==as.Date(MonthEnd)))
  
  # Note: Counter column is used here to specify which row starts MonthStart and MonthEnd_Row.
  # When rows are pulled from year row numbers are also pulled, 
  # so a counter must be used for proper row numbers.
  Start_new <- which(year$Counter==MonthStart_Row)
  End_new <- which(year$Counter==MonthEnd_Row)
  
  # begin nested loop
  for (m in 1:12){
    month_time <- year[Start_new:End_new ,]         #extract data for 3 month timespan within year of interest
    avgmonth_gage <- mean(month_time$`Gage Flow`)   # find average of gage flow for 3 months
    avgmonth_model <- mean(month_time$`Model Flow`) # find average of model flow for 3 months
    AvgMonthlyError[m,1] <- (avgmonth_gage - avgmonth_model)/ avgmonth_gage * 100  # percent error between gage and model
    
    MonthEnd<-as.Date(MonthEnd)
    MonthEnd<-MonthEnd+1
    MonthEndyear <- year(MonthEnd)   # Year associated with last month of extracted data 
    MonthEndmonth <- month(MonthEnd) # Month associated with last month of extracted data 
    
    # the next three lines are for the error calculations -- stop on 1st of month 4 (31 of month 3)
    # Note: this DOES include the 1st of the next month in error calculation
    # Put a control on what date the script advances by - if date is not 1st of month, reset it
    DateCheck <- as.Date(paste0(MonthEndyear,'-',MonthEndmonth,'-01'))
    if (MonthEnd != DateCheck)
      MonthEnd <- as.Date(paste0(MonthEndyear,'-', MonthEndmonth, '-01'))
    
    MonthEnd <- MonthEnd-1
    stopdate <- as.Date(MonthEnd)
    AvgMonthlyError[m,2] <- stopdate
    
    # Advance to next month or count
    MonthStart <- next.month(MonthStart)
    MonthEnd <- MonthEnd+1
    MonthEnd <- next.month(MonthEnd)
    MonthEnd <- MonthEnd-1
    StartMonth_Row <- which(as.Date(all_data$Date)==as.Date(MonthStart));     
    StartMonth_Row <- as.numeric(StartMonth_Row)
    EndMonth_Row <- which(as.Date(all_data$Date)==as.Date(MonthEnd));     
    EndMonth_Row <- as.numeric(EndMonth_Row)
    Start_new <- which(year$Counter==StartMonth_Row)
    End_new <- which(year$Counter==EndMonth_Row)
    m <- m + 1
  }
  
  Timespan_Error[x:y, 1] <- AvgMonthlyError[,1] # save the error entries from AvgMonthlyError
  Timespan_Error[x:y, 2] <- AvgMonthlyError[,2] # save the dates 
  
  # advance Timespan_Error for next run
  x <- x + 12  
  y <- y + 12
  
  YearStart <- as.Date(YearStart) + 365  # Advance 1 year
  YearEnd <- as.Date(YearEnd) + 365     # Advance 1 year & 2 months (from 10-01 to 11-30)
  
  # Put a control on what date the script advances by - if end date is not 11-30, reset it
  # - if begin date is not -10-01, reset it
  YearBeginyear <- year(YearStart)  # pull year of beginning year
  YearBeginCheck <- as.Date(paste0(YearBeginyear,'-10-01'))
  if (YearBeginyear != YearBeginCheck)     
    YearStart <- as.Date(paste0(YearBeginyear,'-10-01'))
  
  YearEndyear <- year(YearEnd)  # pull year of ending year
  YearEndCheck <- as.Date(paste0(YearEndyear,'-11-30'))
  if (YearEnd != YearEndCheck)     
    YearEnd <- as.Date(paste0(YearEndyear,'-11-30'))
  YearStart_Row <- which(as.Date(all_data$Date)== as.Date(YearStart))
  YearEnd_Row <- which(as.Date(all_data$Date) == as.Date(YearEnd))
  
  i <- i + 1
}

# This section of code will plot timeframes with high error.
# count the number of 3 month periods over 20% error, plot the highest 3 periods.

Timespan_Error$Logic <- Timespan_Error$Error>=20 | Timespan_Error$Error<= -20
HighError <- Timespan_Error[Timespan_Error$Logic=='TRUE',]
HighError<- HighError[order(abs(HighError$Error), decreasing = TRUE),]
names(HighError)<-c('Error', 'Date', 'Logic')

# pull data for each of these 3 month segments.
HighestErrors <- HighError[1:3,]
HighestErrors$Date <- as.Date(HighestErrors$Date)

# initalize variables for loop
erroryear <- data.frame(matrix(nrow=1,ncol=6))
errordates <- data.frame(matrix(nrow=1, ncol=2))
names(erroryear)<- c('endyear', 'endmonth', 'enddate', 'startyear', 'startmonth', 'startdate')
names(errordates)<- c('start date row', 'end date row')
storeplotdata1<- data.frame(matrix(nrow=1, ncol=4))
names(storeplotdata1)<- c('Date', 'ModelFlow', 'GageFlow', 'Counter')
storeplotdata2<- data.frame(matrix(nrow=1, ncol=4))
names(storeplotdata2)<- c('Date', 'ModelFlow', 'GageFlow', 'Counter')
storeplotdata3<- data.frame(matrix(nrow=1, ncol=4))
names(storeplotdata3)<- c('Date', 'ModelFlow', 'GageFlow', 'Counter')

q <- 1

for (q in 1:length(HighestErrors)){
  erroryear[q,1] <- year(HighestErrors$Date[q])  # ending year
  erroryear[q,2]<- month(HighestErrors$Date[q]) + 1 # ending month
  erroryear[q,4]<- year(HighestErrors$Date[q]) #startyear
  erroryear[q,5]<- month(HighestErrors$Date[q])-2 #startmonth
  
  if (erroryear[q,2] > 12) { # if end month is jan, must move year up
    erroryear[q,4] <- erroryear[q,1]
    erroryear[q,1]<- erroryear[q,1] + 1 # year for jan moves
    erroryear[q,2] <- 1
  }else if (erroryear[q,5] == -1) {
    erroryear[q,4] <- erroryear[q,4] - 1 # if january, go back a year and start november
    erroryear[q,5] <- 11
  }else if (erroryear[q,5] == 0) {
    erroryear[q,4] <- erroryear[q,4] - 1 # if january, go back a year and start november
    erroryear[q,5] <- 12
  } else{
    erroryear[q,1]<- erroryear[q,1]  #endyear
    erroryear[q,2]<- erroryear[q,2]  #endmonth
    erroryear[q,4]<- erroryear[q,4]  #startyear
    erroryear[q,5]<- erroryear[q,5]  #startmonth
  }
  erroryear[q,3]<- paste0(erroryear[q,1], '-',erroryear[q,2], '-01') #enddate
  erroryear$enddate <- as.Date(erroryear$enddate)
  erroryear[q,6]<- as.Date(paste0(erroryear[q,4], '-', erroryear[q,5], '-01')) #startdate
  erroryear$startdate <- as.Date(erroryear$startdate)
  
  errordates[q,1]<- as.character(erroryear$startdate[q])
  errordates[q,2]<- as.character(erroryear$enddate[q]-1)
  errordates[q,3]<- which(as.Date(all_data$Date)==as.Date(errordates$`start date row`[q]))
  errordates[q,4]<- which(as.Date(all_data$Date)==as.Date(errordates$`end date row`[q]))
  
  plot1<-all_data[errordates$V3[q]:errordates$V4[q],]
if (q==1){
  storeplotdata1<- plot1
}else if(q==2){
  storeplotdata2<- plot1
}else if(q==3){
  storeplotdata3<- plot1
}
  q <- q+1
}

# # create and export 3 plots: \plot for info of row q

error1 <- signif(HighestErrors$Error[1], digits=3)          #Create error variable to display on graph
error2 <- signif(HighestErrors$Error[2], digits=3)
error3 <- signif(HighestErrors$Error[3], digits=3)

# CREATES OUTPUT MATRIX -------------------------------------------------------
# also want to list the number of timespans that were over 20% error.
over20 <- signif(nrow(HighError)/nrow(Timespan_Error)*100, digits=3)
OUTPUT_MATRIX <- matrix(c(avg_gage, avg_model, over20), nrow=1, ncol=3)
rownames(OUTPUT_MATRIX) = c("Area Weighted Flow")
colnames(OUTPUT_MATRIX) = c('USGS', 'Model', 'Error>20 (%)')
overall_error <- signif((OUTPUT_MATRIX[1,1]-OUTPUT_MATRIX[1,2])/OUTPUT_MATRIX[1,1]*100, digits=3)
OUTPUT_MATRIX <- matrix(c(over20, met00_PctError), nrow=1, ncol=2)
rownames(OUTPUT_MATRIX) = c("Percent")
colnames(OUTPUT_MATRIX) = c('Error > 20%', 'Overall Error')

OUTPUT_MATRIX <- round(OUTPUT_MATRIX, digits = 2)
OUTPUT_MATRIXsaver <- OUTPUT_MATRIX
OUTPUT_MATRIX <- kable(format(OUTPUT_MATRIX, digits = 3))
# plot for highest error 
# Max/min for y axis scaling
max <- max(c(max(storeplotdata1$`Gage Flow`), max(storeplotdata1$`Model Flow`)));
min <- min(c(max(storeplotdata1$`Gage Flow`), max(storeplotdata1$`Model Flow`)));
xpos1 <- min(storeplotdata1$Date)+20
xpos2 <- max(storeplotdata1$Date)-20

# Creating and exporting plot
df <- data.frame(as.Date(storeplotdata1$Date), storeplotdata1$`Model Flow`, storeplotdata1$`Gage Flow`); 
colnames(df) <- c('Date', 'Model', 'USGS')
options(scipen=5, width = 1400, height = 950)
error1plot <- ggplot(df, aes(x=Date)) + 
  geom_line(aes(y=USGS, color=name_USGS), size=1) +
  geom_line(aes(y=Model, color=name_model), size=1)+
  theme_bw()+ 
  theme(legend.position="top", 
        legend.title=element_blank(),
        legend.box = "horizontal", 
        legend.background = element_rect(fill="white",
                                         size=0.5, linetype="solid", 
                                         colour ="white"),
        legend.text=element_text(size=14),
        axis.text=element_text(size=14, colour="black"),
        axis.title=element_text(size=14, colour="black"),
        axis.line = element_line(colour = "black", 
                                 size = 0.5, linetype = "solid"),
        axis.ticks = element_line(colour="black"),
        panel.grid.major=element_line(colour = "light grey"), 
        panel.grid.minor=element_blank())+
scale_colour_manual(values=c("black","red"))+
  guides(colour = guide_legend(override.aes = list(size=5)))+
  annotate("text", x=xpos1, y=max, label= paste0('Error:', '',error1, '', '%'), size=5)+
  annotate("text", x=xpos2, y=max, label= paste0('Date Range: ', '', 
             min(storeplotdata1$Date),': ', max(storeplotdata1$Date)), size=5)+
  labs(y = "Flow (cfs)")

# plot for second highest error 
# Max/min for y axis scaling
max <- max(c(max(storeplotdata2$`Gage Flow`), max(storeplotdata2$`Model Flow`)));
min <- min(c(max(storeplotdata2$`Gage Flow`), max(storeplotdata2$`Model Flow`)));
xpos1 <- min(storeplotdata2$Date)+20
xpos2 <- max(storeplotdata2$Date)-20

# Creating and exporting plot
df <- data.frame(as.Date(storeplotdata2$Date), storeplotdata2$`Model Flow`, storeplotdata2$`Gage Flow`); 
colnames(df) <- c('Date', 'Model', 'USGS')
options(scipen=5, width = 1400, height = 950)
error2plot <- ggplot(df, aes(x=Date)) + 
  geom_line(aes(y=USGS, color=name_USGS), size=1) +
  geom_line(aes(y=Model, color=name_model), size=1)+
  theme_bw()+ 
  theme(legend.position="top", 
        legend.title=element_blank(),
        legend.box = "horizontal", 
        legend.background = element_rect(fill="white",
                                         size=0.5, linetype="solid", 
                                         colour ="white"),
        legend.text=element_text(size=14),
        axis.text=element_text(size=14, colour="black"),
        axis.title=element_text(size=14, colour="black"),
        axis.line = element_line(colour = "black", 
                                 size = 0.5, linetype = "solid"),
        axis.ticks = element_line(colour="black"),
        panel.grid.major=element_line(colour = "light grey"), 
        panel.grid.minor=element_blank())+
  scale_colour_manual(values=c("black","red"))+
  guides(colour = guide_legend(override.aes = list(size=5)))+
  annotate("text", x=xpos1, y=max, label= paste0('Error:', '',error2, '', '%'), size=5)+
  annotate("text", x=xpos2, y=max, label= paste0('Date Range: ', '', 
                                                 min(storeplotdata2$Date),': ', max(storeplotdata2$Date)), size=5)+
  labs(y = "Flow (cfs)")



# plot for third highest error 
# Max/min for y axis scaling
max <- max(c(max(storeplotdata3$`Gage Flow`), max(storeplotdata3$`Model Flow`)));
min <- min(c(max(storeplotdata3$`Gage Flow`), max(storeplotdata3$`Model Flow`)));
xpos1 <- min(storeplotdata3$Date)+20
xpos2 <- max(storeplotdata3$Date)-20

# Creating and exporting plot
df <- data.frame(as.Date(storeplotdata3$Date), storeplotdata3$`Model Flow`, storeplotdata3$`Gage Flow`); 
colnames(df) <- c('Date', 'Model', 'USGS')
options(scipen=5, width = 1400, height = 950)
error3plot <- ggplot(df, aes(x=Date)) + 
  geom_line(aes(y=USGS, color=name_USGS), size=1) +
  geom_line(aes(y=Model, color=name_model), size=1)+
  theme_bw()+ 
  theme(legend.position="top", 
        legend.title=element_blank(),
        legend.box = "horizontal", 
        legend.background = element_rect(fill="white",
                                         size=0.5, linetype="solid", 
                                         colour ="white"),
        legend.text=element_text(size=14),
        axis.text=element_text(size=14, colour="black"),
        axis.title=element_text(size=14, colour="black"),
        axis.line = element_line(colour = "black", 
                                 size = 0.5, linetype = "solid"),
        axis.ticks = element_line(colour="black"),
        panel.grid.major=element_line(colour = "light grey"), 
        panel.grid.minor=element_blank())+
  scale_colour_manual(values=c("black","red"))+
  guides(colour = guide_legend(override.aes = list(size=5)))+
  annotate("text", x=xpos1, y=max, label= paste0('Error:', '',error3, '', '%'), size=5)+
  annotate("text", x=xpos2, y=max, label= paste0('Date Range: ', '', 
                                                 min(storeplotdata3$Date),': ', max(storeplotdata3$Date)), size=5)+
  labs(y = "Flow (cfs)")

```
```{r setup, include=FALSE}

# LIBRARIES ---------------------------------------------------------------

library('IHA')
library('PearsonDS')
library('zoo')
library('lubridate')
library('lfstat')
library('ggplot2')
library('scales')
library('IHA')
library('knitr')

# SOURCING CALCULATING FUNCTION -------------------------------------------

source(paste0(container, "\\code\\function_holder.R"));

# CREATE FOLDER -----------------------------------------------------------

dir.create(paste0(container,"\\results\\user's_results\\",siteNo, "_vs_", RivSeg), showWarnings = TRUE)

# LOADING DATA ------------------------------------------------------------

data <- read.csv(paste0(container, container.cont, "\\derived_data\\trimmed+area-adjusted_data\\",siteNo,"_vs_",RivSeg, " - Derived Data.csv"))

# ADDING ADDITIONAL DATA COLUMNS ------------------------------------------
data$year <- year(ymd(data$date))
data$month <- month(ymd(data$date))
data$day <- day(ymd(data$date))

# SETUP FOR CALCULATIONS --------------------------------------------------

# Setup for ___ Day Min Calculations
# Running gage calculations
f3_USGS <- zoo(data$gage.flow, order.by = data$date)
g2_USGS <- group2(f3_USGS, year = 'water')
# Running model calculations
f3_model <- zoo(data$model.flow, order.by = data$date)
g2_model <- group2(f3_model, year = 'water')

# Setup for Monthly Means Calculations
USGS_Monthly_Means <- aggregate(data$gage.flow, list(data$month), FUN = mean)
Model_Monthly_Means <- aggregate(data$model.flow, list(data$month), FUN = mean)

# Setup for Montly Mins Calculations
flows_USGS <- zoo(data$gage.flow, order.by = data$date)
flows_model <- zoo(data$model.flow, order.by = data$date)

# Setup for Flow Exceedance Calculations
# Creating vectors of decreasing flow magnitude
dec_flows_USGS <- sort(data$gage.flow, decreasing = TRUE)
dec_flows_model <- sort(data$model.flow, decreasing = TRUE)
# Determining the "rank" (0-1) of the flow value
num_observations <- as.numeric(length(data$date))
rank_vec <- as.numeric(c(1:num_observations))
# Calculating exceedance probability
prob_exceedance <- 100*((rank_vec) / (num_observations + 1))
# Creating vectors of calculated quantiles
model_prob_exceedance <- quantile(dec_flows_model, probs = c(0.01, 0.05, 0.5, 0.95, 0.99))
USGS_prob_exceedance <- quantile(dec_flows_USGS, probs = c(0.01, 0.05, 0.5, 0.95, 0.99))

# Setup for Sept. 10% Flow
sept_flows <- subset(data, month == '9')
sept_quant_USGS <- quantile(sept_flows$gage.flow, 0.10)
sept_quant_model <- quantile(sept_flows$model.flow, 0.10)

# Setup for Baseflow Calculations
gage.data <- data.frame(data$day, data$month, data$year, data$gage.flow)
names(gage.data) <- c('day', 'month', 'year', 'flow')
model.data <- data.frame(data$day, data$month, data$year, data$model.flow)
names(model.data) <- c('day', 'month', 'year', 'flow')
# Creating lowflow objects
USGSriver <- createlfobj(gage.data, hyearstart = 10, baseflow = TRUE, meta = NULL)
modelriver <- createlfobj(model.data, hyearstart = 10, baseflow = TRUE, meta = NULL)
baseflowriver<- data.frame(modelriver, USGSriver);
colnames(baseflowriver) <-c ('mday', 'mmonth', 'myear', 'mflow', 'mHyear', 'mBaseflow',
                             'gday', 'gmonth', 'gyear', 'gflow', 'gHyear', 'gBaseflow')
# removing NA values
baseflowriver<-baseflowriver[complete.cases(baseflowriver)==TRUE,]
USGSriver<- data.frame(baseflowriver$gday, baseflowriver$gmonth, baseflowriver$gyear, 
                       baseflowriver$gflow, baseflowriver$gHyear, baseflowriver$gBaseflow);
modelriver<- data.frame(baseflowriver$mday, baseflowriver$mmonth, baseflowriver$myear, 
                        baseflowriver$mflow, baseflowriver$mHyear, baseflowriver$mBaseflow)
names(USGSriver) <- c('day', 'month', 'year', 'flow', 'hyear', 'baseflow')
names(modelriver) <- c('day', 'month', 'year', 'flow', 'hyear', 'baseflow')
# Adding date vectors
USGSriver$date <- as.Date(paste0(USGSriver$year,"-",USGSriver$month,"-",USGSriver$day))
modelriver$date <- as.Date(paste0(modelriver$year,"-",modelriver$month,"-",modelriver$day))

# Setup for Low Flows
lf_model <- aggregate(modelriver$flow, by = list(modelriver$hyear), FUN = mean)
lf_USGS <- aggregate(USGSriver$flow, by = list(USGSriver$hyear), FUN = mean)
colnames(lf_model) <- c('Water Year', 'Mean Flow')
colnames(lf_USGS) <- c('Water Year', 'Mean Flow')

# Setup for Residuals
resid <- (data$model.flow - data$gage.flow)
resid <- data.frame(data$date, resid)

# CALCULATIONS ------------------------------------------------------------

# OVERALL MEAN FLOW
met00_Gage_MeanFlow <- signif(mean(data$gage.flow), digits=3);
met00_Model_MeanFlow <- signif(mean(data$model.flow), digits=3);
met00_PctError <- (signif(((met00_Model_MeanFlow - met00_Gage_MeanFlow) / met00_Gage_MeanFlow)*100, digits=3));

# JANUARY LOW FLOW
met01_Gage_JanLF <- signif(fn_iha_mlf(flows_USGS,1), digits=3);
met01_Mod_JanLF <- signif(fn_iha_mlf(flows_model,1), digits=3);
met01_PctError <- (signif(((met01_Mod_JanLF - met01_Gage_JanLF) / met01_Gage_JanLF)*100, digits=3));

# FEBRUARY LOW FLOW
met02_Gage_FebLF <- signif(fn_iha_mlf(flows_USGS,2), digits=3);
met02_Mod_FebLF <- signif(fn_iha_mlf(flows_model,2), digits=3);
met02_PctError <- (signif(((met02_Mod_FebLF - met02_Gage_FebLF) / met02_Gage_FebLF)*100, digits=3));

# MARCH LOW FLOW
met03_Gage_MarLF <- signif(fn_iha_mlf(flows_USGS,3), digits=3);
met03_Mod_MarLF <- signif(fn_iha_mlf(flows_model,3), digits=3);
met03_PctError <- (signif(((met03_Mod_MarLF - met03_Gage_MarLF) / met03_Gage_MarLF)*100, digits=3));

# APRIL LOW FLOW
met04_Gage_AprLF <- signif(fn_iha_mlf(flows_USGS,4), digits=3);
met04_Mod_AprLF <- signif(fn_iha_mlf(flows_model,4), digits=3);
met04_PctError <- (signif(((met04_Mod_AprLF - met04_Gage_AprLF) / met04_Gage_AprLF)*100, digits=3));

# MAY LOW FLOW
met05_Gage_MayLF <- signif(fn_iha_mlf(flows_USGS,5), digits=3);
met05_Mod_MayLF <- signif(fn_iha_mlf(flows_model,5), digits=3);
met05_PctError <- (signif(((met05_Mod_MayLF - met05_Gage_MayLF) / met05_Gage_MayLF)*100, digits=3));

# JUNE LOW FLOW
met06_Gage_JunLF <- signif(fn_iha_mlf(flows_USGS,6), digits=3);
met06_Mod_JunLF <- signif(fn_iha_mlf(flows_model,6), digits=3);
met06_PctError <- (signif(((met06_Mod_JunLF - met06_Gage_JunLF) / met06_Gage_JunLF)*100, digits=3));

# JULY LOW FLOW
met07_Gage_JulLF <- signif(fn_iha_mlf(flows_USGS,7), digits=3);
met07_Mod_JulLF <- signif(fn_iha_mlf(flows_model,7), digits=3);
met07_PctError <- (signif(((met07_Mod_JulLF - met07_Gage_JulLF) / met07_Gage_JulLF)*100, digits=3));

# AUGUST LOW FLOW
met08_Gage_AugLF <- signif(fn_iha_mlf(flows_USGS,8), digits=3);
met08_Mod_AugLF <- signif(fn_iha_mlf(flows_model,8), digits=3);
met08_PctError <- (signif(((met08_Mod_AugLF - met08_Gage_AugLF) / met08_Gage_AugLF)*100, digits=3));

# SEPTEMBER LOW FLOW
met09_Gage_SepLF <- signif(fn_iha_mlf(flows_USGS,9), digits=3);
met09_Mod_SepLF <- signif(fn_iha_mlf(flows_model,9), digits=3);
met09_PctError <- (signif(((met09_Mod_SepLF - met09_Gage_SepLF) / met09_Gage_SepLF)*100, digits=3));

# OCTOBER LOW FLOW
met10_Gage_OctLF <- signif(fn_iha_mlf(flows_USGS,10), digits=3);
met10_Mod_OctLF <- signif(fn_iha_mlf(flows_model,10), digits=3);
met10_PctError <- (signif(((met10_Mod_OctLF - met10_Gage_OctLF) / met10_Gage_OctLF)*100, digits=3));

# NOVEMBER LOW FLOW
met11_Gage_NovLF <- signif(fn_iha_mlf(flows_USGS,11), digits=3);
met11_Mod_NovLF <- signif(fn_iha_mlf(flows_model,11), digits=3);
met11_PctError <- (signif(((met11_Mod_NovLF - met11_Gage_NovLF) / met11_Gage_NovLF)*100, digits=3));

# DECEMBER LOW FLOW
met12_Gage_DecLF <- signif(fn_iha_mlf(flows_USGS,12), digits=3);
met12_Mod_DecLF <- signif(fn_iha_mlf(flows_model,12), digits=3);
met12_PctError <- (signif(((met12_Mod_DecLF - met12_Gage_DecLF) / met12_Gage_DecLF)*100, digits=3));

# JANUARY MEAN FLOW
met13_Gage_JanMF <- signif(USGS_Monthly_Means[1,2], digits=3);
met13_Model_JanMF <- signif(Model_Monthly_Means[1,2], digits=3);
met13_PctError <- (signif(((met13_Model_JanMF - met13_Gage_JanMF) / met13_Gage_JanMF)*100, digits=3));

# FEBRUARY MEAN FLOW
met14_Gage_FebMF <- signif(USGS_Monthly_Means[2,2], digits=3);
met14_Model_FebMF <- signif(Model_Monthly_Means[2,2], digits=3);
met14_PctError <- (signif(((met14_Model_FebMF - met14_Gage_FebMF) / met14_Gage_FebMF)*100, digits=3));

# MARCH MEAN FLOW
met15_Gage_MarMF <- signif(USGS_Monthly_Means[3,2], digits=3);
met15_Model_MarMF <- signif(Model_Monthly_Means[3,2], digits=3);
met15_PctError <- (signif(((met15_Model_MarMF - met15_Gage_MarMF) / met15_Gage_MarMF)*100, digits=3));

# APRIL MEAN FLOW
met16_Gage_AprMF <- signif(USGS_Monthly_Means[4,2], digits=3);
met16_Model_AprMF <- signif(Model_Monthly_Means[4,2], digits=3);
met16_PctError <- (signif(((met16_Model_AprMF - met16_Gage_AprMF) / met16_Gage_AprMF)*100, digits=3));

# MAY MEAN FLOW
met17_Gage_MayMF <- signif(USGS_Monthly_Means[5,2], digits=3);
met17_Model_MayMF <- signif(Model_Monthly_Means[5,2], digits=3);
met17_PctError <- (signif(((met17_Model_MayMF - met17_Gage_MayMF) / met17_Gage_MayMF)*100, digits=3));

# JUNE MEAN FLOW
met18_Gage_JunMF <- signif(USGS_Monthly_Means[6,2], digits=3);
met18_Model_JunMF <- signif(Model_Monthly_Means[6,2], digits=3);
met18_PctError <- (signif(((met18_Model_JunMF - met18_Gage_JunMF) / met18_Gage_JunMF)*100, digits=3));

# JULY MEAN FLOW
met19_Gage_JulMF <- signif(USGS_Monthly_Means[7,2], digits=3);
met19_Model_JulMF <- signif(Model_Monthly_Means[7,2], digits=3);
met19_PctError <- (signif(((met19_Model_JulMF - met19_Gage_JulMF) / met19_Gage_JulMF)*100, digits=3));

# AUGUST MEAN FLOW
met20_Gage_AugMF <- signif(USGS_Monthly_Means[8,2], digits=3);
met20_Model_AugMF <- signif(Model_Monthly_Means[8,2], digits=3);
met20_PctError <- (signif(((met20_Model_AugMF - met20_Gage_AugMF) / met20_Gage_AugMF)*100, digits=3));

# SEPTEMBER MEAN FLOW
met21_Gage_SepMF <- signif(USGS_Monthly_Means[9,2], digits=3);
met21_Model_SepMF <- signif(Model_Monthly_Means[9,2], digits=3);
met21_PctError <- (signif(((met21_Model_SepMF - met21_Gage_SepMF) / met21_Gage_SepMF)*100, digits=3));

# OCTOBER MEAN FLOW
met22_Gage_OctMF <- signif(USGS_Monthly_Means[10,2], digits=3);
met22_Model_OctMF <- signif(Model_Monthly_Means[10,2], digits=3);
met22_PctError <- (signif(((met22_Model_OctMF - met22_Gage_OctMF) / met22_Gage_OctMF)*100, digits=3));

# NOVEMBER MEAN FLOW
met23_Gage_NovMF <- signif(USGS_Monthly_Means[11,2], digits=3);
met23_Model_NovMF <- signif(Model_Monthly_Means[11,2], digits=3);
met23_PctError <- (signif(((met23_Model_NovMF - met23_Gage_NovMF) / met23_Gage_NovMF)*100, digits=3));

# DECEMBER MEAN FLOW
met24_Gage_DecMF <- signif(USGS_Monthly_Means[12,2], digits=3);
met24_Model_DecMF <- signif(Model_Monthly_Means[12,2], digits=3);
met24_PctError <- (signif(((met24_Model_DecMF - met24_Gage_DecMF) / met24_Gage_DecMF)*100, digits=3));

# 1 DAY MIN
yearly_Gage_1DayMin <- g2_USGS[,c(1,2)];
met25_Gage_1DayMinMin <- signif(min(yearly_Gage_1DayMin$`1 Day Min`), digits=3);
yearly_Mod_1DayMin <- g2_model[,c(1,2)];
met25_Mod_1DayMinMin <- signif(min(yearly_Mod_1DayMin$`1 Day Min`), digits=3);
met25_PctError <- (signif(((met25_Mod_1DayMinMin - met25_Gage_1DayMinMin) / met25_Gage_1DayMinMin)*100, digits=3));
met26_Gage_1DayMinMed <- signif(median(yearly_Gage_1DayMin$`1 Day Min`), digits=3);
met26_Mod_1DayMinMed <- signif(median(yearly_Mod_1DayMin$`1 Day Min`), digits=3);
met26_PctError <- (signif(((met26_Mod_1DayMinMed - met26_Gage_1DayMinMed) / met26_Gage_1DayMinMed)*100, digits=3));

# 3 DAY MIN
yearly_Gage_3DayMin <- g2_USGS[,c(1,4)];
met27_Gage_3DayMinMin <- signif(min(yearly_Gage_3DayMin$`3 Day Min`), digits=3);
yearly_Mod_3DayMin <- g2_model[,c(1,4)];
met27_Mod_3DayMinMin <- signif(min(yearly_Mod_3DayMin$`3 Day Min`), digits=3);
met27_PctError <- (signif(((met27_Mod_3DayMinMin - met27_Gage_3DayMinMin) / met27_Gage_3DayMinMin)*100, digits=3));
met28_Gage_3DayMinMed <- signif(median(yearly_Gage_3DayMin$`3 Day Min`), digits=3);
met28_Mod_3DayMinMed <- signif(median(yearly_Mod_3DayMin$`3 Day Min`), digits=3);
met28_PctError <- (signif(((met28_Mod_3DayMinMed - met28_Gage_3DayMinMed) / met28_Gage_3DayMinMed)*100, digits=3));

# 7 DAY MIN
yearly_Gage_7DayMin <- g2_USGS[,c(1,6)];
met29_Gage_7DayMinMin <- signif(min(yearly_Gage_7DayMin$`7 Day Min`), digits=3);
yearly_Mod_7DayMin <- g2_model[,c(1,6)];
met29_Mod_7DayMinMin <- signif(min(yearly_Mod_7DayMin$`7 Day Min`), digits=3);
met29_PctError <- (signif(((met29_Mod_7DayMinMin - met29_Gage_7DayMinMin) / met29_Gage_7DayMinMin)*100, digits=3));
met30_Gage_7DayMinMed <- signif(median(yearly_Gage_7DayMin$`7 Day Min`), digits=3);
met30_Mod_7DayMinMed <- signif(median(yearly_Mod_7DayMin$`7 Day Min`), digits=3);
met30_PctError <- (signif(((met30_Mod_7DayMinMed - met30_Gage_7DayMinMed) / met30_Gage_7DayMinMed)*100, digits=3));

# 30 DAY MIN
yearly_Gage_30DayMin <- g2_USGS[,c(1,8)];
met31_Gage_30DayMinMin <- signif(min(yearly_Gage_30DayMin$`30 Day Min`), digits=3);
yearly_Mod_30DayMin <- g2_model[,c(1,8)];
met31_Mod_30DayMinMin <- signif(min(yearly_Mod_30DayMin$`30 Day Min`), digits=3);
met31_PctError <- (signif(((met31_Mod_30DayMinMin - met31_Gage_30DayMinMin) / met31_Gage_30DayMinMin)*100, digits=3));
met32_Gage_30DayMinMed <- signif(median(yearly_Gage_30DayMin$`30 Day Min`), digits=3);
met32_Mod_30DayMinMed <- signif(median(yearly_Mod_30DayMin$`30 Day Min`), digits=3);
met32_PctError <- (signif(((met32_Mod_30DayMinMed - met32_Gage_30DayMinMed) / met32_Gage_30DayMinMed)*100, digits=3));

# 90 DAY MIN
yearly_Gage_90DayMin <- g2_USGS[,c(1,10)];
met33_Gage_90DayMinMin <- signif(min(yearly_Gage_90DayMin$`90 Day Min`), digits=3);
yearly_Mod_90DayMin <- g2_model[,c(1,10)];
met33_Mod_90DayMinMin <- signif(min(yearly_Mod_90DayMin$`90 Day Min`), digits=3);
met33_PctError <- (signif(((met33_Mod_90DayMinMin - met33_Gage_90DayMinMin) / met33_Gage_90DayMinMin)*100, digits=3));
met34_Gage_90DayMinMed <- signif(median(yearly_Gage_90DayMin$`90 Day Min`), digits=3);
met34_Mod_90DayMinMed <- signif(median(yearly_Mod_90DayMin$`90 Day Min`), digits=3);
met34_PctError <- (signif(((met34_Mod_90DayMinMed - met34_Gage_90DayMinMed) / met34_Gage_90DayMinMed)*100, digits=3));

# 7Q10
met35_Gage_7Q10 <- signif(fn_iha_7q10(flows_USGS), digits=3);
met35_Model_7Q10 <- signif(fn_iha_7q10(flows_model), digits=3);
met35_PctError <- (signif(((met35_Model_7Q10 - met35_Gage_7Q10) / met35_Gage_7Q10)*100, digits=3));

# DROUGHT OF RECORD (MIN. 90 DAY MIN.) YEAR
met37_Gage_DoR <- fn_iha_DOR_Year(flows_USGS);
met37_Model_DoR <- fn_iha_DOR_Year(flows_model);
if (met37_Gage_DoR == met37_Model_DoR) {
  met37_PctError <- 0;
} else {
  met37_PctError <- 100;
}

# 1% Non-exceedance Flow
met38_Gage_1NonEx <- signif(USGS_prob_exceedance[["1%"]], digits=3);
met38_Model_1NonEx <- signif(model_prob_exceedance[["1%"]], digits=3);
met38_PctError <- (signif(((met38_Model_1NonEx - met38_Gage_1NonEx) / met38_Gage_1NonEx)*100, digits=3));

# 5% Non-exceedance Flow
met39_Gage_5NonEx <- signif(USGS_prob_exceedance[["5%"]], digits=3);
met39_Model_5NonEx <- signif(model_prob_exceedance[["5%"]], digits=3);
met39_PctError <- (signif(((met39_Model_5NonEx - met39_Gage_5NonEx) / met39_Gage_5NonEx)*100, digits=3));

# 50% Non-exceedance Flow
met40_Gage_50NonEx <- signif(USGS_prob_exceedance[["50%"]], digits=3);
met40_Model_50NonEx <- signif(model_prob_exceedance[["50%"]], digits=3);
met40_PctError <- (signif(((met40_Model_50NonEx - met40_Gage_50NonEx) / met40_Gage_50NonEx)*100, digits=3));

# 95% Non-exceedance Flow
met41_Gage_95NonEx <- signif(USGS_prob_exceedance[["95%"]], digits=3);
met41_Model_95NonEx <- signif(model_prob_exceedance[["95%"]], digits=3);
met41_PctError <- (signif(((met41_Model_95NonEx - met41_Gage_95NonEx) / met41_Gage_95NonEx)*100, digits=3));

# 99% Non-exceedance Flow
met42_Gage_99NonEx <- signif(USGS_prob_exceedance[["99%"]], digits=3);
met42_Model_99NonEx <- signif(model_prob_exceedance[["99%"]], digits=3);
met42_PctError <- (signif(((met42_Model_99NonEx - met42_Gage_99NonEx) / met42_Gage_99NonEx)*100, digits=3));

# Sept. 10% Flow
met43_Gage_Sep10 <- signif(sept_quant_USGS[["10%"]], digits=3);
met43_Model_Sep10 <- signif(sept_quant_model[["10%"]], digits=3);
met43_PctError <- (signif(((met43_Model_Sep10 - met43_Gage_Sep10) / met43_Gage_Sep10)*100, digits=3));

# Baseflow (Average)
met44_Gage_Base <- signif(mean(USGSriver$baseflow), digits=3);
met44_Model_Base <- signif(mean(modelriver$baseflow), digits=3);
met44_PctError <- (signif(((met44_Model_Base - met44_Gage_Base) / met44_Gage_Base)*100, digits=3));

# JANUARY HIGH FLOW
met45_Gage_JanHF <- signif(fn_iha_mhf(flows_USGS,1), digits=3);
met45_Mod_JanHF <- signif(fn_iha_mhf(flows_model,1), digits=3);
met45_PctError <- (signif(((met45_Mod_JanHF - met45_Gage_JanHF) / met45_Gage_JanHF)*100, digits=3));

# FEBRUARY HIGH FLOW
met46_Gage_FebHF <- signif(fn_iha_mhf(flows_USGS,2), digits=3);
met46_Mod_FebHF <- signif(fn_iha_mhf(flows_model,2), digits=3);
met46_PctError <- (signif(((met46_Mod_FebHF - met46_Gage_FebHF) / met46_Gage_FebHF)*100, digits=3));

# MARCH HIGH FLOW
met47_Gage_MarHF <- signif(fn_iha_mhf(flows_USGS,3), digits=3);
met47_Mod_MarHF <- signif(fn_iha_mhf(flows_model,3), digits=3);
met47_PctError <- (signif(((met47_Mod_MarHF - met47_Gage_MarHF) / met47_Gage_MarHF)*100, digits=3));

# APRIL HIGH FLOW
met48_Gage_AprHF <- signif(fn_iha_mhf(flows_USGS,4), digits=3);
met48_Mod_AprHF <- signif(fn_iha_mhf(flows_model,4), digits=3);
met48_PctError <- (signif(((met48_Mod_AprHF - met48_Gage_AprHF) / met48_Gage_AprHF)*100, digits=3));

# MAY HIGH FLOW
met49_Gage_MayHF <- signif(fn_iha_mhf(flows_USGS,5), digits=3);
met49_Mod_MayHF <- signif(fn_iha_mhf(flows_model,5), digits=3);
met49_PctError <- (signif(((met49_Mod_MayHF - met49_Gage_MayHF) / met49_Gage_MayHF)*100, digits=3));

# JUNE HIGH FLOW
met50_Gage_JunHF <- signif(fn_iha_mhf(flows_USGS,6), digits=3);
met50_Mod_JunHF <- signif(fn_iha_mhf(flows_model,6), digits=3);
met50_PctError <- (signif(((met50_Mod_JunHF - met50_Gage_JunHF) / met50_Gage_JunHF)*100, digits=3));

# JULY HIGH FLOW
met51_Gage_JulHF <- signif(fn_iha_mhf(flows_USGS,7), digits=3);
met51_Mod_JulHF <- signif(fn_iha_mhf(flows_model,7), digits=3);
met51_PctError <- (signif(((met51_Mod_JulHF - met51_Gage_JulHF) / met51_Gage_JulHF)*100, digits=3));

# AUGUST HIGH FLOW
met52_Gage_AugHF <- signif(fn_iha_mhf(flows_USGS,8), digits=3);
met52_Mod_AugHF <- signif(fn_iha_mhf(flows_model,8), digits=3);
met52_PctError <- (signif(((met52_Mod_AugHF - met52_Gage_AugHF) / met52_Gage_AugHF)*100, digits=3));

# SEPTEMBER HIGH FLOW
met53_Gage_SepHF <- signif(fn_iha_mhf(flows_USGS,9), digits=3);
met53_Mod_SepHF <- signif(fn_iha_mhf(flows_model,9), digits=3);
met53_PctError <- (signif(((met53_Mod_SepHF - met53_Gage_SepHF) / met53_Gage_SepHF)*100, digits=3));

# OCTOBER HIGH FLOW
met54_Gage_OctHF <- signif(fn_iha_mhf(flows_USGS,10), digits=3);
met54_Mod_OctHF <- signif(fn_iha_mhf(flows_model,10), digits=3);
met54_PctError <- (signif(((met54_Mod_OctHF - met54_Gage_OctHF) / met54_Gage_OctHF)*100, digits=3));

# NOVEMBER HIGH FLOW
met55_Gage_NovHF <- signif(fn_iha_mhf(flows_USGS,11), digits=3);
met55_Mod_NovHF <- signif(fn_iha_mhf(flows_model,11), digits=3);
met55_PctError <- (signif(((met55_Mod_NovHF - met55_Gage_NovHF) / met55_Gage_NovHF)*100, digits=3));

# DECEMBER HIGH FLOW
met56_Gage_DecHF <- signif(fn_iha_mhf(flows_USGS,12), digits=3);
met56_Mod_DecHF <- signif(fn_iha_mhf(flows_model,12), digits=3);
met56_PctError <- (signif(((met56_Mod_DecHF - met56_Gage_DecHF) / met56_Gage_DecHF)*100, digits=3));

# 1 DAY MAX
yearly_Gage_1DayMax <- g2_USGS[,c(1,3)];
met57_Gage_1DayMaxMax <- signif(max(yearly_Gage_1DayMax$`1 Day Max`), digits=3);
yearly_Mod_1DayMax <- g2_model[,c(1,3)];
met57_Mod_1DayMaxMax <- signif(max(yearly_Mod_1DayMax$`1 Day Max`), digits=3);
met57_PctError <- (signif(((met57_Mod_1DayMaxMax - met57_Gage_1DayMaxMax) / met57_Gage_1DayMaxMax)*100, digits=3));
met58_Gage_1DayMaxMed <- signif(median(yearly_Gage_1DayMax$`1 Day Max`), digits=3);
met58_Mod_1DayMaxMed <- signif(median(yearly_Mod_1DayMax$`1 Day Max`), digits=3);
met58_PctError <- (signif(((met58_Mod_1DayMaxMed - met58_Gage_1DayMaxMed) / met58_Gage_1DayMaxMed)*100, digits=3));

# 3 DAY MAX
yearly_Gage_3DayMax <- g2_USGS[,c(1,5)];
met59_Gage_3DayMaxMax <- signif(max(yearly_Gage_3DayMax$`3 Day Max`), digits=3);
yearly_Mod_3DayMax <- g2_model[,c(1,5)];
met59_Mod_3DayMaxMax <- signif(max(yearly_Mod_3DayMax$`3 Day Max`), digits=3);
met59_PctError <- (signif(((met59_Mod_3DayMaxMax - met59_Gage_3DayMaxMax) / met59_Gage_3DayMaxMax)*100, digits=3));
met60_Gage_3DayMaxMed <- signif(median(yearly_Gage_3DayMax$`3 Day Max`), digits=3);
met60_Mod_3DayMaxMed <- signif(median(yearly_Mod_3DayMax$`3 Day Max`), digits=3);
met60_PctError <- (signif(((met60_Mod_3DayMaxMed - met60_Gage_3DayMaxMed) / met60_Gage_3DayMaxMed)*100, digits=3));

# 7 DAY MAX
yearly_Gage_7DayMax <- g2_USGS[,c(1,7)];
met61_Gage_7DayMaxMax <- signif(max(yearly_Gage_7DayMax$`7 Day Max`), digits=3);
yearly_Mod_7DayMax <- g2_model[,c(1,7)];
met61_Mod_7DayMaxMax <- signif(max(yearly_Mod_7DayMax$`7 Day Max`), digits=3);
met61_PctError <- (signif(((met61_Mod_7DayMaxMax - met61_Gage_7DayMaxMax) / met61_Gage_7DayMaxMax)*100, digits=3));
met62_Gage_7DayMaxMed <- signif(median(yearly_Gage_7DayMax$`7 Day Max`), digits=3);
met62_Mod_7DayMaxMed <- signif(median(yearly_Mod_7DayMax$`7 Day Max`), digits=3);
met62_PctError <- (signif(((met62_Mod_7DayMaxMed - met62_Gage_7DayMaxMed) / met62_Gage_7DayMaxMed)*100, digits=3));

# 30 DAY MAX
yearly_Gage_30DayMax <- g2_USGS[,c(1,9)];
met63_Gage_30DayMaxMax <- signif(max(yearly_Gage_30DayMax$`30 Day Max`), digits=3);
yearly_Mod_30DayMax <- g2_model[,c(1,9)];
met63_Mod_30DayMaxMax <- signif(max(yearly_Mod_30DayMax$`30 Day Max`), digits=3);
met63_PctError <- (signif(((met63_Mod_30DayMaxMax - met63_Gage_30DayMaxMax) / met63_Gage_30DayMaxMax)*100, digits=3));
met64_Gage_30DayMaxMed <- signif(median(yearly_Gage_30DayMax$`30 Day Max`), digits=3);
met64_Mod_30DayMaxMed <- signif(median(yearly_Mod_30DayMax$`30 Day Max`), digits=3);
met64_PctError <- (signif(((met64_Mod_30DayMaxMed - met64_Gage_30DayMaxMed) / met64_Gage_30DayMaxMed)*100, digits=3));

# 90 DAY MAX
yearly_Gage_90DayMax <- g2_USGS[,c(1,11)];
met65_Gage_90DayMaxMax <- signif(max(yearly_Gage_90DayMax$`90 Day Max`), digits=3);
yearly_Mod_90DayMax <- g2_model[,c(1,11)];
met65_Mod_90DayMaxMax <- signif(max(yearly_Mod_90DayMax$`90 Day Max`), digits=3);
met65_PctError <- (signif(((met65_Mod_90DayMaxMax - met65_Gage_90DayMaxMax) / met65_Gage_90DayMaxMax)*100, digits=3));
met66_Gage_90DayMaxMed <- signif(median(yearly_Gage_90DayMax$`90 Day Max`), digits=3);
met66_Mod_90DayMaxMed <- signif(median(yearly_Mod_90DayMax$`90 Day Max`), digits=3);
met66_PctError <- (signif(((met66_Mod_90DayMaxMed - met66_Gage_90DayMaxMed) / met66_Gage_90DayMaxMed)*100, digits=3));

# LOW YEARLY MEAN
lf_USGS_flow <- which(lf_USGS$`Water Year` == met37_Gage_DoR)
lf_USGS_flow <- lf_USGS$`Mean Flow`[lf_USGS_flow]
lf_model_flow <- which(lf_model$`Water Year`== met37_Gage_DoR)
lf_model_flow <- lf_model$`Mean Flow`[lf_model_flow]
met67_model_lfmin <- signif(lf_model_flow, digits = 3)
met67_USGS_lfmin <- signif(lf_USGS_flow, digits = 3)
met67_PctError <- (signif(((met67_model_lfmin - met67_USGS_lfmin) / met67_USGS_lfmin)*100, digits=3));
# Table 1: Monthly Average Flow
Table1 <- matrix(c(met00_Gage_MeanFlow, met13_Gage_JanMF, met14_Gage_FebMF,
                   met15_Gage_MarMF, met16_Gage_AprMF, met17_Gage_MayMF,
                   met18_Gage_JunMF, met19_Gage_JulMF, met20_Gage_AugMF,
                   met21_Gage_SepMF, met22_Gage_OctMF, met23_Gage_NovMF,
                   met24_Gage_DecMF, met00_Model_MeanFlow, met13_Model_JanMF,
                   met14_Model_FebMF, met15_Model_MarMF, met16_Model_AprMF,
                   met17_Model_MayMF, met18_Model_JunMF, met19_Model_JulMF,
                   met20_Model_AugMF, met21_Model_SepMF, met22_Model_OctMF,
                   met23_Model_NovMF, met24_Model_DecMF, met00_PctError,
                   met13_PctError, met14_PctError, met15_PctError,
                   met16_PctError, met17_PctError, met18_PctError,
                   met19_PctError, met20_PctError, met21_PctError,
                   met22_PctError, met23_PctError, met24_PctError),
                 nrow = 13, ncol = 3);
colnames(Table1) = c("USGS Gage", "Model", "Pct. Error");
rownames(Table1) = c("Overall Mean Flow", 
                     "Jan. Mean Flow", "Feb. Mean Flow",
                     "Mar. Mean Flow", "Apr. Mean Flow",
                     "May Mean Flow", "Jun. Mean Flow",
                     "Jul. Mean Flow", "Aug. Mean Flow",
                     "Sep. Mean Flow", "Oct. Mean Flow",
                     "Nov. Mean Flow", "Dec. Mean Flow");
Table1 <- round(Table1, digits = 2)
Table1 <- kable(format(Table1, digits = 3, drop0trailing = TRUE))
Table2 <- matrix(c(met01_Gage_JanLF, met02_Gage_FebLF, met03_Gage_MarLF,
                   met04_Gage_AprLF, met05_Gage_MayLF, met06_Gage_JunLF,
                   met07_Gage_JulLF, met08_Gage_AugLF, met09_Gage_SepLF,
                   met10_Gage_OctLF, met11_Gage_NovLF, met12_Gage_DecLF,
                   met01_Mod_JanLF, met02_Mod_FebLF, met03_Mod_MarLF, 
                   met04_Mod_AprLF, met05_Mod_MayLF, met06_Mod_JunLF,
                   met07_Mod_JulLF, met08_Mod_AugLF, met09_Mod_SepLF,
                   met10_Mod_OctLF, met11_Mod_NovLF, met12_Mod_DecLF,
                   met01_PctError, met02_PctError, met03_PctError,
                   met04_PctError, met05_PctError, met06_PctError,
                   met07_PctError, met08_PctError, met09_PctError,
                   met10_PctError, met11_PctError, met12_PctError),
                 nrow = 12, ncol = 3);
colnames(Table2) = c("USGS Gage", "Model", "Pct. Error");
rownames(Table2) = c("Jan. Low Flow", "Feb. Low Flow",
                     "Mar. Low Flow", "Apr. Low Flow",
                     "May Low Flow", "Jun. Low Flow",
                     "Jul. Low Flow", "Aug. Low Flow",
                     "Sep. Low Flow", "Oct. Low Flow",
                     "Nov. Low Flow", "Dec. Low Flow");
Table2 <- round(Table2, digits = 2)
Table2 <- kable(format(Table2, digits = 3, drop0trailing = TRUE))
# Table 3: Monthly High Flow
Table3 <- matrix(c(met45_Gage_JanHF, met46_Gage_FebHF, met47_Gage_MarHF,
                   met48_Gage_AprHF, met49_Gage_MayHF, met50_Gage_JunHF,
                   met51_Gage_JulHF, met52_Gage_AugHF, met53_Gage_SepHF,
                   met54_Gage_OctHF, met55_Gage_NovHF, met56_Gage_DecHF,
                   met45_Mod_JanHF, met46_Mod_FebHF, met47_Mod_MarHF,
                   met48_Mod_AprHF, met49_Mod_MayHF, met50_Mod_JunHF,
                   met51_Mod_JulHF, met52_Mod_AugHF, met53_Mod_SepHF,
                   met54_Mod_OctHF, met55_Mod_NovHF, met56_Mod_DecHF,
                   met45_PctError, met46_PctError, met47_PctError,
                   met48_PctError, met49_PctError, met50_PctError,
                   met51_PctError, met52_PctError, met53_PctError,
                   met54_PctError, met55_PctError, met56_PctError),
                 nrow = 12, ncol = 3);
colnames(Table3) = c("USGS Gage", "Model", "Pct. Error");
rownames(Table3) = c("Jan. High Flow", "Feb. High Flow",
                     "Mar. High Flow", "Apr. High Flow",
                     "May High Flow", "Jun. High Flow",
                     "Jul. High Flow", "Aug. High Flow",
                     "Sep. High Flow", "Oct. High Flow",
                     "Nov. High Flow", "Dec. High Flow");
Table3 <- round(Table3, digits = 2)
Table3 <- kable(format(Table3, digits = 3, drop0trailing = TRUE))
Table4 <- matrix(c(met25_Gage_1DayMinMin, met26_Gage_1DayMinMed,
                   met27_Gage_3DayMinMin, met28_Gage_3DayMinMed,
                   met29_Gage_7DayMinMin, met30_Gage_7DayMinMed,
                   met31_Gage_30DayMinMin, met32_Gage_30DayMinMed,
                   met33_Gage_90DayMinMin, met34_Gage_90DayMinMed,
                   met35_Gage_7Q10, met37_Gage_DoR,
                   met67_USGS_lfmin, met44_Gage_Base, 
                   met25_Mod_1DayMinMin, met26_Mod_1DayMinMed,
                   met27_Mod_3DayMinMin, met28_Mod_3DayMinMed,
                   met29_Mod_7DayMinMin, met30_Mod_7DayMinMed,
                   met31_Mod_30DayMinMin, met32_Mod_30DayMinMed,
                   met33_Mod_90DayMinMin, met34_Mod_90DayMinMed,
                   met35_Model_7Q10, met37_Model_DoR,
                   met67_model_lfmin, met44_Model_Base, 
                   met25_PctError, met26_PctError, met27_PctError,
                   met28_PctError, met29_PctError, met30_PctError,
                   met31_PctError, met32_PctError, met33_PctError,
                   met34_PctError, met35_PctError,
                   met37_PctError, met67_PctError, met44_PctError), 
                 nrow = 14, ncol = 3);
colnames(Table4) = c("USGS Gage", "Model", "Pct. Error");
rownames(Table4) = c("Min. 1 Day Min", "Med. 1 Day Min", 
                     "Min. 3 Day Min", "Med. 3 Day Min",
                     "Min. 7 Day Min", "Med. 7 Day Min",
                     "Min. 30 Day Min", "Med. 30 Day Min",
                     "Min. 90 Day Min", "Med. 90 Day Min", 
                     "7Q10", "Year of 90-Day Min. Flow",
                     "Drought Year Mean", "Mean Baseflow");
Table4 <- round(Table4, digits = 2)
Table4 <- kable(format(Table4, digits = 3, drop0trailing = TRUE))
# Table 5: Period High Flows
Table5 <- matrix(c(met57_Gage_1DayMaxMax, met58_Gage_1DayMaxMed,
                   met59_Gage_3DayMaxMax, met60_Gage_3DayMaxMed,
                   met61_Gage_7DayMaxMax, met62_Gage_7DayMaxMed,
                   met63_Gage_30DayMaxMax, met64_Gage_30DayMaxMed,
                   met65_Gage_90DayMaxMax, met66_Gage_90DayMaxMed,
                   met57_Mod_1DayMaxMax, met58_Mod_1DayMaxMed,
                   met59_Mod_3DayMaxMax, met60_Mod_3DayMaxMed,
                   met61_Mod_7DayMaxMax, met62_Mod_7DayMaxMed,
                   met63_Mod_30DayMaxMax, met64_Mod_30DayMaxMed,
                   met65_Mod_90DayMaxMax, met66_Mod_90DayMaxMed,
                   met57_PctError, met58_PctError,
                   met59_PctError, met60_PctError,
                   met61_PctError, met62_PctError,
                   met63_PctError, met64_PctError,
                   met65_PctError, met66_PctError), 
                 nrow = 10, ncol = 3);
colnames(Table5) = c("USGS Gage", "Model", "Pct. Error");
rownames(Table5) = c("Max. 1 Day Max", "Med. 1 Day Max", 
                     "Max. 3 Day Max", "Med. 3 Day Max",
                     "Max. 7 Day Max", "Med. 7 Day Max",
                     "Max. 30 Day Max", "Med. 30 Day Max",
                     "Max. 90 Day Max", "Med. 90 Day Max");
Table5 <- round(Table5, digits = 2)
Table5 <- kable(format(Table5, digits = 3, drop0trailing = TRUE))
# Table 6: Non-Exceedance Flows
Table6 <- matrix(c(met38_Gage_1NonEx, met39_Gage_5NonEx, met40_Gage_50NonEx,
                   met41_Gage_95NonEx, met42_Gage_99NonEx, met43_Gage_Sep10,
                   met38_Model_1NonEx, met39_Model_5NonEx, met40_Model_50NonEx,
                   met41_Model_95NonEx, met42_Model_99NonEx, met43_Model_Sep10,
                   met38_PctError, met39_PctError, met40_PctError,
                   met41_PctError, met42_PctError, met43_PctError), nrow = 6, ncol = 3);
colnames(Table6) = c("USGS Gage", "Model", "Pct. Error");
rownames(Table6) = c("1% Non-Exceedance", "5% Non-Exceedance",
                     "50% Non-Exceedance", "95% Non-Exceedance",
                     "99% Non-Exceedance", "Sept. 10% Non-Exceedance");
Table6 <- round(Table6, digits = 2)
Table6 <- kable(format(Table6, digits = 3, drop0trailing = TRUE))
# Creating names for plot legends
name_USGS <- paste('Gage', siteNo);
name_model <- paste('Model: River Seg.\n', RivSeg);

# CREATE FUNCTIONS FOR PLOTTING  ------------------------------------------
base_breaks <- function(n = 10){
  function(x) {
    axisTicks(log10(range(x, na.rm = TRUE)), log = TRUE, n = n)
  }
}
scaleFUN <- function(x) sprintf("%.0f", x)

```



```{r, echo=FALSE, warning=FALSE, message=FALSE}
gis_img
```

```{r, results = 'asis', echo=FALSE, warning=FALSE, message=FALSE}
description.cont <- paste0(" The average daily discharge error between the model and gage data for the 20 year timespan was ", OUTPUT_MATRIXsaver[1,2] ,"%, with ", OUTPUT_MATRIXsaver[1,1], "% of its rolling three month time spans above 20% error.")
cat(description)
cat(description.cont)
```

\pagebreak

## Table 1: Monthly Low Flows
```{r, echo=FALSE, warning=FALSE, message=FALSE}
Table2
```

## Table 2: Monthly Average Flows
```{r, echo=FALSE, warning=FALSE, message=FALSE}
Table1
```


\pagebreak

## Table 3: Monthly High Flows
```{r, echo=FALSE, warning=FALSE, message=FALSE}
Table3
```

## Table 4: Period Low Flows
```{r, echo=FALSE, warning=FALSE, message=FALSE}
Table4
```

## Table 5: Period High Flows
```{r, echo=FALSE, warning=FALSE, message=FALSE}
Table5
```

## Table 6: Non-Exceedance Flows
```{r, echo=FALSE, warning=FALSE, message=FALSE}
Table6
```

## Fig. 1: Hydrograph
```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Basic hydrograph -----
# Max/min for y axis scaling
max <- max(c(max(data$gage.flow), max(data$model.flow)));
min <- min(c(min(data$gage.flow), max(data$model.flow)));
if (max > 10000){
  max <- 100000
}else if (max > 1000){
  max <- 10000
}else if (max > 100){
  max <- 1000
}else if (max > 10){
  max <- 100
}
if (min>100){
  min<-100
}else if (min>10){ 
  min<-10
}else 
  min<-1
if (min==100){
  fixtheyscale<- scale_y_continuous(trans = log_trans(), 
                                    breaks = c(100, 1000, 10000, 100000), 
                                    limits=c(min,max))
}else if (min==10){
  fixtheyscale<- scale_y_continuous(trans = log_trans(), 
                                    breaks = c(10, 100, 1000, 10000), 
                                    limits=c(min,max))
}else if (min==1){
  fixtheyscale<- scale_y_continuous(trans = log_trans(), 
                                    breaks = c(1, 10, 100, 1000, 10000), 
                                    limits=c(min,max))
}else
  fixtheyscale<- scale_y_continuous(trans = log_trans(), breaks = base_breaks(), 
                                    labels=scaleFUN, limits=c(min,max))
df <- data.frame(as.Date(data$date), data$model.flow, data$gage.flow); 
colnames(df) <- c('Date', 'Model', 'USGS')
options(scipen=5, width = 1400, height = 950)
myplot <- ggplot(df, aes(x=Date)) + 
  geom_line(aes(y=USGS, color=name_USGS), size=0.5) +
  geom_line(aes(y=Model, color=name_model), size=0.5)+
  fixtheyscale+
  theme_bw()+ 
  theme(legend.position="top", 
        legend.title=element_blank(),
        legend.box = "horizontal", 
        legend.background = element_rect(fill="white",
                                         size=0.5, linetype="solid", 
                                         colour ="white"),
        legend.text=element_text(size=12),
        axis.text=element_text(size=12, colour="black"),
        axis.title=element_text(size=14, colour="black"),
        axis.line = element_line(colour = "black", 
                                 size = 0.5, linetype = "solid"),
        axis.ticks = element_line(colour="black"),
        panel.grid.major=element_line(colour = "light grey"), 
        panel.grid.minor=element_blank())+
  scale_colour_manual(values=c("black","red"))+
  guides(colour = guide_legend(override.aes = list(size=5)))+
  labs(y = "Flow (cfs)")
myplot
```

# Fig. 2: Zoomed Hydrograph
```{r, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
# Zoomed hydrograph in year of lowest 90-year flow -----
# Running gage calculations
f3_USGS <- zoo(data$gage.flow, order.by = data$date)
g2_USGS <- group2(f3_USGS, year = 'water')
# Running model calculations
f3_model <- zoo(data$model.flow, order.by = data$date)
g2_model <- group2(f3_model, year = 'water')

yearly_Gage_90DayMin <- g2_USGS[,c(1,10)];
yearly_Mod_90DayMin <- g2_model[,c(1,10)];
low.year <- subset(yearly_Gage_90DayMin, yearly_Gage_90DayMin$`90 Day Min`==min(yearly_Gage_90DayMin$`90 Day Min`));
low.year <- low.year$year;
low.year <- subset(data, data$year==low.year);

# Scaling using max/min
max <- max(c(max(low.year$gage.flow), max(low.year$model.flow)));
min <- min(c(min(low.year$gage.flow), min(low.year$model.flow)));
if (max > 10000){
  max <- 100000
}else if (max > 1000){
  max <- 10000
}else if (max > 100){
  max <- 1000
}else if (max > 10){
  max <- 100
}
if (min>100){
  min<-100
}else if (min>10){ 
  min<-10
}else 
  min<-1
if (min==100){
  fixtheyscale<- scale_y_continuous(trans = log_trans(), 
                                    breaks = c(100, 1000, 10000, 100000), 
                                    limits=c(min,max))
}else if (min==10){
  fixtheyscale<- scale_y_continuous(trans = log_trans(), 
                                    breaks = c(10, 100, 1000, 10000), 
                                    limits=c(min,max))
}else if (min==1){
  fixtheyscale<- scale_y_continuous(trans = log_trans(), 
                                    breaks = c(1, 10, 100, 1000, 10000), 
                                    limits=c(min,max))
}else
  fixtheyscale<- scale_y_continuous(trans = log_trans(), breaks = base_breaks(), 
                                    labels=scaleFUN, limits=c(min,max))
df <- data.frame(as.Date(low.year$date), low.year$model.flow, low.year$gage.flow); 
colnames(df) <- c('Date', 'Model', 'USGS')
options(scipen=5, width = 1400, height = 950)
myplot <- ggplot(df, aes(x=Date)) + 
  geom_line(aes(y=USGS, color=name_USGS), size=0.7) +
  geom_line(aes(y=Model, color=name_model), size=0.7)+
  fixtheyscale+ 
  theme_bw()+ 
  theme(legend.position="top", 
        legend.title=element_blank(),
        legend.box = "horizontal", 
        legend.background = element_rect(fill="white",
                                         size=0.5, linetype="solid", 
                                         colour ="white"),
        legend.text=element_text(size=12),
        axis.text=element_text(size=12, colour="black"),
        axis.title=element_text(size=14, colour="black"),
        axis.line = element_line(colour = "black", 
                                 size = 0.5, linetype = "solid"),
        axis.ticks = element_line(colour="black"),
        panel.grid.major=element_line(colour = "light grey"), 
        panel.grid.minor=element_blank())+
  scale_colour_manual(values=c("black","red"))+
  guides(colour = guide_legend(override.aes = list(size=5)))+
  labs(y = "Flow (cfs)")
print <- try(print(myplot))
```
```{r, echo=FALSE, warning=FALSE, message=FALSE}
if (class(print)=="try-error") {
  low.year2 <- subset(yearly_Gage_90DayMin, yearly_Gage_90DayMin$`90 Day Min`==sort(yearly_Gage_90DayMin$`90 Day Min`, TRUE)[2]);
  low.year2 <- low.year2$year;
  low.year2 <- subset(data, data$year==low.year2);
  
  # Scaling using max/min
  max2 <- max(c(max(low.year2$gage.flow), max(low.year2$model.flow)));
  min2 <- min(c(min(low.year2$gage.flow), min(low.year2$model.flow)));
  if (max2 > 10000){
    max2 <- 100000
  }else if (max2 > 1000){
    max2 <- 10000
  }else if (max2 > 100){
    max2 <- 1000
  }else if (max2 > 10){
    max2 <- 100
  }
  if (min2>100){
    min2<-100
  }else if (min2>10){ 
    min2<-10
  }else {
    min2<-1
  }
  if (min2==100){
    fixtheyscale2<- scale_y_continuous(trans = log_trans(), 
                                       breaks = c(100, 1000, 10000, 100000), 
                                       limits=c(min2,max2))
  }else if (min2==10){
    fixtheyscale2<- scale_y_continuous(trans = log_trans(), 
                                       breaks = c(10, 100, 1000, 10000), 
                                       limits=c(min2,max2))
  }else if (min2==1){
    fixtheyscale2<- scale_y_continuous(trans = log_trans(), 
                                       breaks = c(1, 10, 100, 1000, 10000), 
                                       limits=c(min2,max2))
  }else{
    fixtheyscale2<- scale_y_continuous(trans = log_trans(), breaks = base_breaks(), 
                                       labels=scaleFUN, limits=c(min2,max2))
  }
  # Creating and exporting plot
  png(filename=paste0(container,"\\results\\user's_results\\",siteNo,"_vs_",RivSeg,
                      "\\plots\\Fig. 7 - Zoomed Hydrograph.png"),
      width = 1400, height = 600, units = "px");
  
  df2 <- data.frame(as.Date(low.year2$date), low.year2$model.flow, low.year2$gage.flow); 
  colnames(df2) <- c('Date', 'Model', 'USGS')
  
  options(scipen=5, width = 1400, height = 950)
myplot2 <- ggplot(df2, aes(x=Date)) + 
  geom_line(aes(y=USGS, color=name_USGS), size=0.7) +
  geom_line(aes(y=Model, color=name_model), size=0.7)+
  fixtheyscale2+ 
  theme_bw()+ 
  theme(legend.position="top", 
        legend.title=element_blank(),
        legend.box = "horizontal", 
        legend.background = element_rect(fill="white",
                                         size=0.5, linetype="solid", 
                                         colour ="white"),
        legend.text=element_text(size=12),
        axis.text=element_text(size=12, colour="black"),
        axis.title=element_text(size=14, colour="black"),
        axis.line = element_line(colour = "black", 
                                 size = 0.5, linetype = "solid"),
        axis.ticks = element_line(colour="black"),
        panel.grid.major=element_line(colour = "light grey"), 
        panel.grid.minor=element_blank())+
  scale_colour_manual(values=c("black","red"))+
  guides(colour = guide_legend(override.aes = list(size=5)))+
  labs(y = "Flow (cfs)")
  dev.off()
  myplot2
} else {
  myplot
}
```

# Fig. 3: Flow Exceedance
```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Flow exceedance plot -----
# Determining max flow value for exceedance plot scale
max <- max(c(max(dec_flows_model), max(dec_flows_USGS)));
min <- min(c(min(dec_flows_model), min(dec_flows_USGS)));

if (max > 10000){
  max <- 100000
}else if (max > 1000){
  max <- 10000
}else if (max > 100){
  max <- 1000
}else if (max > 10){
  max <- 100
}
if (min>100){
  min<-100
}else if (min>10){ 
  min<-10
}else 
  min<-1
if (min==100){
  fixtheyscale<- scale_y_continuous(trans = log_trans(), 
                                    breaks = c(100, 1000, 10000, 100000), 
                                    limits=c(min,max))
}else if (min==10){
  fixtheyscale<- scale_y_continuous(trans = log_trans(), 
                                    breaks = c(10, 100, 1000, 10000), 
                                    limits=c(min,max))
}else if (min==1){
  fixtheyscale<- scale_y_continuous(trans = log_trans(), 
                                    breaks = c(1, 10, 100, 1000, 10000), 
                                    limits=c(min,max))
}else
  fixtheyscale<- scale_y_continuous(trans = log_trans(), breaks = base_breaks(), 
                                    labels=scaleFUN, limits=c(min,max))
df <- data.frame(prob_exceedance, dec_flows_model, dec_flows_USGS); 
colnames(df) <- c('Date', 'Model', 'USGS')
options(scipen=5, width = 1400, height = 950)
myplot <- ggplot(df, aes(x=Date)) + 
  geom_line(aes(y=USGS, color=name_USGS), size=0.8) +
  geom_line(aes(y=Model, color=name_model), size=0.8)+
  fixtheyscale+ 
  theme_bw()+ 
  theme(legend.position="top", 
        legend.title=element_blank(),
        legend.box = "horizontal", 
        legend.background = element_rect(fill="white",
                                         size=0.5, linetype="solid", 
                                         colour ="white"),
        legend.text=element_text(size=12),
        axis.text=element_text(size=12, colour="black"),
        axis.title=element_text(size=14, colour="black"),
        axis.line = element_line(colour = "black", 
                                 size = 0.5, linetype = "solid"),
        axis.ticks = element_line(colour="black"),
        panel.grid.major=element_line(colour = "light grey"), 
        panel.grid.minor=element_blank())+
  scale_colour_manual(values=c("black","red"))+
  guides(colour = guide_legend(override.aes = list(size=5)))+
  labs(x= "Probability of Exceedance (%)", y = "Flow (cfs)")
myplot
```

# Fig. 4: Baseflow
```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Baseflow Indiviudal Graph -----
# Determining max flow value for plot scale
max <- max(c(max(USGSriver$baseflow), max(modelriver$baseflow), max(USGSriver$flow), max(modelriver$flow)));
min <- min(c(min(USGSriver$baseflow), min(modelriver$baseflow), min(USGSriver$flow), min(modelriver$flow)));

if (max > 10000){
  max <- 100000
}else if (max > 1000){
  max <- 10000
}else if (max > 100){
  max <- 1000
}else if (max > 10){
  max <- 100
}
if (min>100){
  min<-100
}else if (min>10){ 
  min<-10
}else 
  min<-1
if (min==100){
  fixtheyscale<- scale_y_continuous(trans = log_trans(), 
                                    breaks = c(100, 1000, 10000, 100000), 
                                    limits=c(min,max))
}else if (min==10){
  fixtheyscale<- scale_y_continuous(trans = log_trans(), 
                                    breaks = c(10, 100, 1000, 10000), 
                                    limits=c(min,max))
}else if (min==1){
  fixtheyscale<- scale_y_continuous(trans = log_trans(), 
                                    breaks = c(1, 10, 100, 1000, 10000), 
                                    limits=c(min,max))
}else
  fixtheyscale<- scale_y_continuous(trans = log_trans(), breaks = base_breaks(), 
                                    labels=scaleFUN, limits=c(min,max))
df <- data.frame(as.Date(modelriver$date), modelriver$baseflow, USGSriver$baseflow, modelriver$flow, USGSriver$flow); 
colnames(df) <- c('Date', 'ModelBaseflow', 'USGSBaseflow', 'ModelFlow', 'USGSFlow')
options(scipen=5, width = 1400, height = 950)
myplot <- ggplot(df, aes(x=Date)) + 
  geom_line(aes(y=USGSBaseflow, color=name_USGS), size=0.5) +
  geom_line(aes(y=ModelBaseflow, color=name_model), size=0.5)+
  fixtheyscale+ 
  theme_bw()+ 
  theme(legend.position="top", 
        legend.title=element_blank(),
        legend.box = "horizontal", 
        legend.background = element_rect(fill="white",
                                         size=0.5, linetype="solid", 
                                         colour ="white"),
        legend.text=element_text(size=12),
        axis.text=element_text(size=12, colour="black"),
        axis.title=element_text(size=14, colour="black"),
        axis.line = element_line(colour = "black", 
                                 size = 0.5, linetype = "solid"),
        axis.ticks = element_line(colour="black"),
        panel.grid.major=element_line(colour = "light grey"), 
        panel.grid.minor=element_blank())+
  scale_colour_manual(values=c("black","red"))+
  guides(colour = guide_legend(override.aes = list(size=5)))+
  labs(y = "Flow (cfs)")
myplot
```

# Fig. 5: Combined Baseflow
```{r, echo=FALSE, warning=FALSE, message=FALSE}
par(mfrow = c(1,1));
options(scipen=5, width = 1400, height = 950)
myplot <- ggplot(df, aes(x=Date)) + 
  geom_line(aes(y=USGSFlow, color=paste("Gage Flow")), size=1)+
  geom_line(aes(y=ModelFlow, color=paste("Model Flow")), size=0.5)+ 
  geom_line(aes(y=USGSBaseflow, color=paste("Gage Baseflow")), size=0.5) +
  geom_line(aes(y=ModelBaseflow, color=paste("Model Baseflow")), size=1)+
  fixtheyscale+ 
  theme_bw()+ 
  theme(legend.position="top", 
        legend.title=element_blank(),
        legend.box = "horizontal", 
        legend.background = element_rect(fill="white",
                                         size=0.5, linetype="solid", 
                                         colour ="white"),
        legend.text=element_text(size=12),
        axis.text=element_text(size=12, colour="black"),
        axis.title=element_text(size=14, colour="black"),
        axis.line = element_line(colour = "black", 
                                 size = 0.5, linetype = "solid"),
        axis.ticks = element_line(colour="black"),
        panel.grid.major=element_line(colour = "light grey"), 
        panel.grid.minor=element_blank())+
  scale_colour_manual(values=c("black","grey","red", "light pink"))+
  guides(colour = guide_legend(override.aes = list(size=5)))+
  labs(y = "Flow (cfs)")
myplot
```



# Fig. 6: Largest Error Segment
```{r, echo=FALSE, warning=FALSE, message=FALSE}
error1plot
```

# Fig. 7: Second Largest Error Segment
```{r, echo=FALSE, warning=FALSE, message=FALSE}
error2plot
```

# Fig. 8: Third Largest Error Segment
```{r, echo=FALSE, warning=FALSE, message=FALSE}
error3plot
```

# Fig. 9: Residuals Plot
```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Setup for Residuals
resid <- (data$model.flow - data$gage.flow)
resid <- data.frame(data$date, resid)

# Residuals plot for hydrograph

zeroline <- rep_len(0, length(data$date)) 
quantresid <- data.frame(signif(quantile(resid$resid), digits=3))
min <- min(resid$resid)
max <- max(resid$resid)
names(quantresid) <- c('Percentiles')

df <- data.frame(as.Date(resid$data.date), resid$resid, zeroline); 
colnames(df) <- c('Date', 'Residual', 'Zeroline')
options(scipen=5, width = 1400, height = 950)
myplot <- ggplot(df, aes(x=Date)) + 
  geom_point(aes(y=Residual, color="Residual (Model - Gage)"), size=1) +
  geom_line(aes(y=Zeroline, color="Zero Line"), size=0.8)+
  scale_y_continuous(limits=c(min,max))+ 
  theme_bw()+ 
  theme(legend.position="top", 
        legend.title=element_blank(),
        legend.box = "horizontal", 
        legend.background = element_rect(fill="white",
                                         size=0.5, linetype="solid", 
                                         colour ="white"),
        legend.text=element_text(size=12),
        axis.text=element_text(size=12, colour="black"),
        axis.title=element_text(size=14, colour="black"),
        axis.line = element_line(colour = "black", 
                                 size = 0.5, linetype = "solid"),
        axis.ticks = element_line(colour="black"),
        panel.grid.major=element_line(colour = "light grey"), 
        panel.grid.minor=element_blank())+
  scale_colour_manual(values=c("dark green","black"))+
  guides(colour = guide_legend(override.aes = list(size=5)))+
  labs(y = "Flow Difference (cfs)")
myplot
```